---
title: "Bachelorarbeit: Introduction"
author: "Patrick Bigler"
date: "2023-07-07"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
```

## Read files

Here, we read all digitized data sets. For a comprehensive analysis, it is
important to have enough data. Therefore, only data sets containing more
than 40 measurements are used. The following data sets were not considered
in the analyisis:

-   Bassour (only 13 measurements)

-   Mt. Whitney (only 5 Measurements)

-   Mt.Wilson (only 5 Measurements)

-   Mt. Wilson (only 20Measurements)

-   Mt. Wilson (only 18 Measurements)

```{r Read_all_data, message=FALSE, error=FALSE, warning=FALSE}

Montezuma.1920.1930 <- read.delim("../Data/Montezuma.txt")

Harqua_Hala.1920.1925 <- read.delim("../Data/Harqua_Hala.txt")

Mt.Wilson.1905.1920 <- read.delim("../Data/Mt_Wilson_1.txt")

Washington.1903.1907 <- read.delim("../Data/Washington_2.txt")

Hump_Mountain.1917.1918 <- read.delim("../Data/Hump_Mountain.txt")

Calama.1918.1920 <- read.delim("../Data/Calama.txt")

Mt.Brukkaros.1926.1930 <- read.delim("../Data/Mt_Brukkaros.txt")

Table.mountain.1925.1930 <- read.delim("../Data/Table_mountain.txt")
```

## Coordinates-Transformation

Here, we transform coordinates in the WGS84 system

```{r coordinates_transformation, message=FALSE, error=FALSE, warning=FALSE}
source("../R/function.coordinate.transformation.R")
Katmai.lat <- coordinates.transfomation(58, 16, 43)
Katmai.lon <- coordinates.transfomation(-154, -57, -24.9)

Santa.Maria.lat <- coordinates.transfomation(14, 45, 20)
Santa.Maria.lon <- coordinates.transfomation(-91, -33, -6)

katla.lat <- coordinates.transfomation(63, 37, 50)
katla.lon <- coordinates.transfomation(-19, -3, -0)

ksudach.lat <- coordinates.transfomation(51, 48, 26)
ksudach.lon <- coordinates.transfomation(157, 32, 3)

raikoke.lat <- coordinates.transfomation(48, 17, 30)
raikoke.lon <- coordinates.transfomation(153, 14, 30)

Montezuma.lat <- coordinates.transfomation(-22, -40, -0)
Montezuma.lon <- coordinates.transfomation(-68, -56, -0)

Calama.lat <- coordinates.transfomation(-22, -28, -0)
Calama.lon <- coordinates.transfomation(-68, -56, -0)

Table.Mountain.lat <- coordinates.transfomation(34, 22, 0)
Table.Mountain.lon <- coordinates.transfomation(-117, -41, -0)

Harqua.Hala.lat <- coordinates.transfomation(33, 48, 0)
Harqua.Hala.lon <- coordinates.transfomation(-113, -20, 0)

Mount.Brukkaros.lat <- coordinates.transfomation(-25, -52, -0)
Mount.Brukkoras.lon <- coordinates.transfomation(17, 48, 0)

Mount.Wilson.lat <- coordinates.transfomation(34, 12, 55)
Mount.Wilson.lon <- coordinates.transfomation(-118, -17, -29)

Washington.lat <- coordinates.transfomation(38, 53, 17.3)
Washingtons.lon <- coordinates.transfomation(-77, -01, -33.6)

Hump.Mountain.lat <- coordinates.transfomation(36, 8, 0)
Hump.Mountain.lon <- coordinates.transfomation(-82, 0, 0)

antarctica.lat <- -79.47
antarctica.lon <- -112.09

greenland.lat <- 77.45
greenland.lon <- -51.06
```

## Visualize the locations

### Summary of all locations

Here, we create a tibble for all location. We need that for mapping the
locations.

```{r mapping_preparation, message=FALSE, error=FALSE, warning=FALSE}
df.locations <- tibble("Location" =
c("WDC06A", "NEEM-S1" ,"Novarupta", "Santa Maria", "Katla", "Ksudach", "Raikoke", "Montezuma",
"Calama", "Table Mountain", "Harqua Hala",
"Mt. Brukkaros", "Mt. Wilson",
"Washington","Hump Mountain"),
"latitude" =
c(antarctica.lat,greenland.lat ,Katmai.lat, Santa.Maria.lat, katla.lat, ksudach.lat, raikoke.lat, Montezuma.lat,
Calama.lat, Table.Mountain.lat, Harqua.Hala.lat,
Mount.Brukkaros.lat,
Mount.Wilson.lat, Washington.lat,
Hump.Mountain.lat),
"longitude" =
c(antarctica.lon, greenland.lon  ,Katmai.lon, Santa.Maria.lon, katla.lon , ksudach.lon, raikoke.lon , Montezuma.lon,
Calama.lon, Table.Mountain.lon, Harqua.Hala.lon,
Mount.Brukkoras.lon,
Mount.Wilson.lon, Washingtons.lon,
Hump.Mountain.lon),
"Altitude" =
c(NA, NA ,2047, 3772, 1512, 1079, 551, 2711, 2250, 2286, 1721,
1586, 1727, 10, 2250),
"Legend" =
c(rep("Ice core",2) ,rep("Volcano",5), rep("Observation station", 8)))
```

### Mapping all locations

```{r mapping_locations, message=FALSE, error=FALSE, warning=FALSE}
#read the world map
world_map <- map_data("world")
# map the locations

overview.plot <- ggplot() +
  geom_map(data = world_map, map = world_map,
  aes(long, lat, map_id = region),
  color = "white", fill = "lightgray", size = 0.1) +
  geom_point(data = df.locations, aes(x = `longitude`, y = `latitude`,
  color = Legend), size = 0.5) +
  scale_y_continuous(limits = c(-80, 80)) +
  scale_x_continuous(limits = c(-180, 180)) +
  labs(x = "Longitude [deg]", y = "Latitude [deg]") +
  theme_light() +
  geom_label_repel(aes(x = df.locations$longitude, y = df.locations$latitude ,
  label = df.locations$Location, color = df.locations$Legend,
  size = NULL), nudge_y = 1.5, nudge_x = 1.5, box.padding = 0.35, point.padding = 0.5,
  min.segment.length = 0.01, segment.color = 'black', max.overlaps = Inf, show.legend = FALSE,
  max.time = 5, max.iter = 100000) +
  guides(color = guide_legend(override.aes = list(size = 3) ) )+
  theme(legend.background = element_rect(fill = "white", linewidth = 0.5, 
                                       linetype = "solid", colour = "black")) +
  theme(legend.position = c(.98, .035),
      legend.justification = c("right", "bottom"), legend.box.just = "right",
      legend.margin = margin(6, 6, 6, 6)) +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))


overview.plot

pdf('../analysis/General/map.pdf',
    width = 8, height = 5)
overview.plot
dev.off()
```

# Theoretical Values

```{r}
#function for theoretical calculation
source('../R/General/theoretical_transmission.R')

# Create a sequenze with wavelenth between 0.1nm and 1.6nm
wavelenghts <- seq(from = 0.1, to = 1.6, by = 0.01)

# Create a sequenze with wavelengths and zenith angle
values <- transmittance(wavelenghts)

# Put all values in a tibble
theoretical.values <- tibble("lambda" = wavelenghts,
                             'normal irradiation' = values)
```

# Analyses of the various locations

Here you can find all analyzed locations. Run the code of the desired
location and you will be automatically redirected to the desired document.
Further, you will find a very brief summary of the time-period and the
volcanic events.

## Washington (1902 - 1907)

Contains 44 measurements between 1902 - 1907 and information about the
tropical eruption of Santa Maria in 1902-10-24.

```{r open_washington}
file.edit('../vignettes/Analyses/Washington.Rmd')
```

## Mt. Wilson (1905 - 1920)

Contains 1245 measurements between 1905 - 1920 and information about the
following high latitude eruptions: Ksudach in 1907-03-28, Novarupta in
1912-06-06 and Katla in 1918-10-12.

```{r open_mt.wilson}
file.edit('../vignettes/Analyses/Mt.Wilson.Rmd')
```

## Hump Mountain (1917 -1918)

Contains 58 measurements between 1917 - 1918 and information about the high
latitude eruption of Katla in 1918-10-12.

```{r open_hump_mountain}
file.edit('../vignettes/Analyses/Hump_Mountain.Rmd')
```

## Calama (1918 - 1920)

Contains 226 measurements between 1920 - 1925 and information about the
high latitude eruption of Katla in 1918-10-12.

```{r open_calama}
file.edit('../vignettes/Analyses/Calama.Rmd')
```

## Haraqua Hala (1920 - 1925)

Contains 226 measurements between 1920 - 1925 and information about the
high latitude eruption of Raikoke in 1924-02-15.

```{r open_haraqua_hala}
file.edit('../vignettes/Analyses/Haraqua_Hala.Rmd')
```

## Montezuma (1920 - 1930)

Contains 462 measurements between 1920 - 1930 and information about the
high latitude eruption of Raikoke in 1924-02-15.

```{r open_montezuma}
file.edit('../vignettes/Analyses/Montezuma.Rmd')
```

## Table Mountain (1925 - 1930)

Contains 445 measurements between 1925 - 1930 and information about the
high latitude eruption of Raikoke in 1924-02-15.

```{r open_table_mountain}
file.edit('../vignettes/Analyses/Table_Mountain.Rmd')
```

## Mt. Brukkaros (1926 - 1930)

Contains 203 measurements between 1926 - 1930 and information about the
high latitude eruption of Raikoke in 1924-02-15.

```{r open_Mt.Brukkaros}
file.edit('../vignettes/Analyses/Mt_Brukkaros.Rmd')
```
