---
title: "Bachelorarbeit: Washington"
author: "Patrick Bigler"
date: "2023-09-02"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

```{r message=FALSE, error=FALSE, warning=FALSE}
source("../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
```

## Read data

```{r}
Washington.1902.1904 <- read.delim("../Data/Washington_1.txt")

Washington.1903.1907 <- read.delim("../Data/Washington_2.txt")

################################################################################
# Washington
################################################################################

Washington.1902.1904 <- Washington.1902.1904|>
  dplyr::mutate('Date' = lubridate::ymd(paste(year, month, day, sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Washington.1902.1904$Location)))|>
  dplyr::select(-c('year', 'month', 'day'))


Washington.1902.1904 <- replace(Washington.1902.1904, Washington.1902.1904 == -999, NA)

################################################################################

Washington.1903.1907 <- Washington.1903.1907|>
  dplyr::mutate('Date' = lubridate::ymd(paste(year, month, day, sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Washington.1903.1907$Location)))|>  
  dplyr::select(-c('year', 'month', 'day'))

Washington.1903.1907 <- replace(Washington.1903.1907, Washington.1903.1907 == -999, NA)
```

## Slice and rebuild

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Mt.Wilson}

Washington <- Washington.1902.1904|>
  dplyr::rename('lambda_400' = 'lambda1...m.', 'lambda_450' = 'lambda2...m.',
                'lambda_500' = 'lambda3...m.', 'lambda_600' = 'lambda4...m.',
                'lambda_700' = 'lambda5...m.','lambda_800' = 'lambda6...m.',
                'lambda_900' = 'lambda7...m.','lambda_1000' = 'lambda8...m.',
                'lambda_1200' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_400' = 'transmission1....100.', 'trans_450' = 'transmission2....100.',
                'trans_500' = 'transmission3....100.','trans_600' = 'transmission4....100.',
                'trans_700' = 'transmission5....100.','trans_800' = 'transmission6....100.',
                'trans_900' = 'transmission7....100.','trans_1000' = 'transmission8....100.',
                'trans_1200' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date','lambda_400','trans_400',
                  'lambda_450','trans_450', 'lambda_500', 'trans_500', 
                  'lambda_600', 'trans_600', 'lambda_700', 'trans_700', 
                  'lambda_800', 'trans_800', 'lambda_900', 'trans_900', 
                  'lambda_1000', 'trans_1000',
                  'lambda_1200', 'trans_1200', 'lambda_1600', 'trans_1600'))



# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Washington <- Washington|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))
```

## Dataquality

-   Transform data frame into a long format.

-   Set levels

-   Substitute strange values with NA

```{r}

################################################################################
# Transmission (long format)
################################################################################

Washington_long <- Washington|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('400', '450', '500', '600', '700', 
                                 '800','900', '1000', '1200', '1600'), times = 44))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))

################################################################################

prep.mean <- Washington|>
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date, 
                   '400' = mean(trans_400, na.rm = TRUE),                   
                   '450' = mean(trans_450, na.rm = TRUE),                  
                   '500' = mean(trans_500, na.rm = TRUE),                   
                   '600' = mean(trans_600, na.rm = TRUE),                   
                   '700' = mean(trans_700, na.rm = TRUE),                   
                   '800' = mean(trans_800, na.rm = TRUE),   
                   '1000' = mean(trans_1000, na.rm = TRUE), 
                   '1200' = mean(trans_1200, na.rm = TRUE),                   
                   '1600' = mean(trans_1600, na.rm = TRUE))|>
  dplyr::select(c('Date','month', ends_with('0'))) |>
  pivot_longer(cols = ends_with('0'), 
               names_to = 'variable', values_to = 'value')


prep.std <- Washington|>
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date,
                   std_400 = sd(trans_400, na.rm = TRUE),                   
                   std_450 = sd(trans_450, na.rm = TRUE),                  
                   std_500 = sd(trans_500, na.rm = TRUE),                                                         std_600 = sd(trans_600, na.rm = TRUE),                   
                   std_700 = sd(trans_700, na.rm = TRUE),                   
                   std_800 = sd(trans_800, na.rm = TRUE),   
                   std_1000 = sd(trans_1000, na.rm = TRUE), 
                   std_1200 = sd(trans_1200, na.rm = TRUE),                   
                   std_1600 = sd(trans_1600, na.rm = TRUE))|>
  dplyr::select(c('Date','month', starts_with('std'))) |>
  pivot_longer(cols = starts_with(c('std')), 
               names_to = 'variable', values_to = 'value')

transmission <- inner_join(prep.mean, prep.std, by = 'Date') |>
  dplyr::rename('month' = 'month.x',
                'variable' = 'variable.x',
                'mean' = 'value.x',
                'std' = 'value.y')|>
  dplyr::select(c('month', 'variable', 'mean', 'std'))|>
  group_by(month, variable)|>
  dplyr::summarise(mean = mean(mean),
                   std = mean(std))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("350", "400", "450", "500", 
                           "600", "700", "800",
                           "000", "1200", "1600"))) |>
  dplyr::filter(variable == '350' | variable == '400' | variable == '450' |
                  variable == '600' | variable == '700' | variable == '1600')

################################################################################

trans_annual_mean <- Washington|>
  dplyr::select(c('row','Date', starts_with('t'))) |>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise('350' = mean(trans_350, na.rm = TRUE),
                   '400' = mean(trans_400, na.rm = TRUE),
                   '450' = mean(trans_450, na.rm = TRUE),
                   '500' = mean(trans_500, na.rm = TRUE),
                   '600' = mean(trans_600, na.rm = TRUE),
                   '700' = mean(trans_700, na.rm = TRUE),
                   '800' = mean(trans_800, na.rm = TRUE),
                   '1200' = mean(trans_1200, na.rm = TRUE),
                   '1600' = mean(trans_1600, na.rm = TRUE))|>
  pivot_longer(cols = ends_with('0'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("350", "400", "450", "500", 
                           "600", "700", "800",
                           "1000", "1200", "1600")))

################################################################################
# Optical Depth
################################################################################

Washington_od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))

################################################################################

prep.mean.od <- Washington|>
  dplyr::mutate_at(c('trans_400', 'trans_450', 'trans_500', 
                     'trans_600', 'trans_700', 'trans_800'
                     , 'trans_1000', 'trans_1200', 'trans_1600'), ~-log(.)) |>    
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date,
                   '400' = mean(trans_400, na.rm = TRUE),                   
                   '450' = mean(trans_450, na.rm = TRUE),                  
                   '500' = mean(trans_500, na.rm = TRUE),                   
                   '600' = mean(trans_600, na.rm = TRUE),                   
                   '700' = mean(trans_700, na.rm = TRUE),                   
                   '800' = mean(trans_800, na.rm = TRUE),   
                   '1000' = mean(trans_1000, na.rm = TRUE), 
                   '1200' = mean(trans_1200, na.rm = TRUE),                   
                   '1600' = mean(trans_1600, na.rm = TRUE))|>
  dplyr::select(c('Date','month', ends_with('0'))) |>
  pivot_longer(cols = ends_with('0'), 
               names_to = 'variable', values_to = 'value')

prep.std.od <- Washington|>
  dplyr::mutate_at(c('trans_400', 'trans_450', 'trans_500', 
                     'trans_600', 'trans_700', 'trans_800'
                     , 'trans_1000', 'trans_1200', 'trans_1600'), ~-log(.)) |>  
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date,
                   std_400 = sd(trans_400, na.rm = TRUE),                   
                   std_450 = sd(trans_450, na.rm = TRUE),                  
                   std_500 = sd(trans_500, na.rm = TRUE),                                                         std_600 = sd(trans_600, na.rm = TRUE),                   
                   std_700 = sd(trans_700, na.rm = TRUE),                   
                   std_800 = sd(trans_800, na.rm = TRUE),   
                   std_1000 = sd(trans_1000, na.rm = TRUE), 
                   std_1200 = sd(trans_1200, na.rm = TRUE),                   
                   std_1600 = sd(trans_1600, na.rm = TRUE))|>
  dplyr::select(c('Date','month', starts_with('std'))) |>
  pivot_longer(cols = starts_with(c('std')), 
               names_to = 'variable', values_to = 'value')


optical_depth <- inner_join(prep.mean.od, prep.std.od, by = 'Date') |>
  dplyr::rename('month' = 'month.x',
                'variable' = 'variable.x',
                'mean' = 'value.x',
                'std' = 'value.y')|>
  dplyr::select(c('month', 'variable', 'mean', 'std'))|>
  group_by(month, variable)|>
  dplyr::summarise(mean = mean(mean),
                   std = mean(std))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("400", "450", "500", 
                           "600", "700", "800",
                           "1000", "1200", "1600"))) |>
  dplyr::filter(variable == '400' | variable == '450' |
                  variable == '600' | variable == '1600')

################################################################################

od_annual_mean <- Washington|>
  dplyr::select(c('row','Date', starts_with('t'))) |>
  dplyr::mutate_at(c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800",
                           "trans_1000", "trans_1200", "trans_1600"), ~-log(.)) |>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise('400' = mean(trans_400, na.rm = TRUE),
                   '450' = mean(trans_450, na.rm = TRUE),
                   '500' = mean(trans_500, na.rm = TRUE),
                   '600' = mean(trans_600, na.rm = TRUE),
                   '700' = mean(trans_700, na.rm = TRUE),
                   '800' = mean(trans_800, na.rm = TRUE),
                   '1200' = mean(trans_1200, na.rm = TRUE),
                   '1600' = mean(trans_1600, na.rm = TRUE))|>
  pivot_longer(cols = ends_with('0'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("400", "450", "500", 
                           "600", "700", "800",
                           "1000", "1200", "1600")))

################################################################################
# Ågström parameter
################################################################################

Washington.alpha <- Washington|>
  dplyr::mutate(
    alpha_400 = -(log(Washington$trans_400) - log(Washington$trans_1000)) / log(400),
    alpha_450 = -(log(Washington$trans_450) - log(Washington$trans_1000)) / log(450),
    alpha_500 = -(log(Washington$trans_500) - log(Washington$trans_1000)) / log(500),
    alpha_600 = -(log(Washington$trans_600) - log(Washington$trans_1000)) / log(600),
    alpha_700 = -(log(Washington$trans_700) - log(Washington$trans_1000)) / log(700),
    alpha_800 = -(log(Washington$trans_800) - log(Washington$trans_1000)) / log(800),
    alpha_900 = -(log(Washington$trans_900) - log(Washington$trans_1000)) / log(900),
    alpha_1200 = -(log(Washington$trans_1200) - log(Washington$trans_1000)) / log(1200),
    alpha_1600 = -(log(Washington$trans_1600) - log(Washington$trans_1000)) / log(1600)) |>
  dplyr::select(c('row','Date', starts_with('a')))

################################################################################

Washington.alpha.long <- Washington.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1000", "alpha_1200", "alpha_1600")))

################################################################################

alpha_annual_mean <- Washington.alpha|>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise('400' = mean(alpha_400, na.rm = TRUE),
                   '450' = mean(alpha_450, na.rm = TRUE),
                   '500' = mean(alpha_500, na.rm = TRUE),
                   '600' = mean(alpha_600, na.rm = TRUE),
                   '700' = mean(alpha_700, na.rm = TRUE),
                   '800' = mean(alpha_800, na.rm = TRUE),
                   '1200' = mean(alpha_1200, na.rm = TRUE),
                   '1600' = mean(alpha_1600, na.rm = TRUE))|>
  pivot_longer(cols = ends_with('0'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("400", "450", "500", 
                           "600", "700", "800",
                           "1000", "1200", "1600")))
```

# Graphs

## Transmission

### Overview transmission

```{r message=FALSE, warning=FALSE, error=FALSE}

################################################################################
# Overview (1902 - 1903)

Washington.1902.1903.trans <- Washington_long|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  geom_rect(aes(xmin = as.Date("1902-10-02", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +  
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [1902-10-24]", hjust = 0, vjust = -0.2, angle = 90) + 
  labs(x = 'Date [year]', y = 'Transmittance [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.1902.1903.trans

################################################################################
# Zoom in (year 1912)
  
Washington.1903.trans <- Washington_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1903-01-01') & Date < as_date('1903-12-31')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90) +
  labs(x = 'Months [1912]', y = 'Transmittance [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))


Washington.1903.trans



```

### Boxplot

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}

Washington.boxplot <- Washington_long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot
```

### Monthly aggregated atmospheric transmission

```{r transmissio_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}

transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - std, ymax = mean + std), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [May - Nov]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r annual_transmission ,message=FALSE, warning=FALSE, error=FALSE}

annual_transmission <- trans_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 0, label= "Novarupta [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0, label= "Novarupta [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [1907-03-28]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [1905 - 1920]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1905 - 1920)

Washington.1905.1920.od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +  
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90) + 
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90) +  
  labs(x = 'Date [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

Washington.1905.1920.od

################################################################################
# Zoom in (year 1912)

Washington.1912.od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(Date > as_date('1912-01-01') & Date < as_date('1913-01-01')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90) +
  labs(x = 'Months [1912]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))    

Washington.1912.od 
```

### Boxplot

```{r}
Washington.boxplot.od <- Washington_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
    dplyr::filter(variable  != 'trans_900') |>  
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot.od
```

### Monthly aggregated optical depth

```{r}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - std, ymax = mean + std), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [May - Nov]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r}

annual_od <- od_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [1905 - 1920]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1.2))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1905 - 1920)

Washington.alpha.1905.1920 <- Washingtonalpha.long|>
  dplyr::filter(variable  != 'alpha_900') |>  
  ggplot()+
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 0.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +  
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +  
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 0.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90) + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novaruptu [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90) +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90) +  
  labs(x = 'Date [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.alpha.1905.1920

################################################################################
# Zoom in (year 1912)

Mt.Wilson.1912.alpha <- Mt.Wilson.alpha.long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1912-01-01') & Date < as_date('1913-01-01')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90) +
  labs(x = 'Months [1912]', y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))


Washington.1912.alpha

```

### Boxplot

```{r}
Washington.boxplot.alpha <- Washington.alpha.long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r  message=FALSE, error=FALSE, warning=FALSE}

angstrom_overview <- Washington.alpha.long|>
  dplyr::filter(Date > as_date('1912-05-01') & Date < as_date('1913-01-01'))|>
    dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = -.15, label= "Novarupta [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  labs(x = 'Time [1912]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('350','400','450','500',
                                                     '600','700','800','1200','1600')) +
  scale_y_continuous(limits = c(-.15, .15))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = .2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = .2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = .2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = .2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = .2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = .2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [1905 - 1920]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(0, .2))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r}

pdf('../analysis/Washington//Transmission/Mt.Wilson.boxplot.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot
dev.off()

pdf('../analysis/Washington//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../analysis/Washington//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()

pdf('../analysis/Washington//Transmission/Mt.Wilson.1905.1920.trans.pdf',
    width = 8, height = 5)
Mt.Wilson.1905.1920.trans
dev.off()

pdf('../analysis/Washington//Transmission/Mt.Wilson.1912.trans.pdf',
    width = 8, height = 5)
Mt.Wilson.1912.trans
dev.off()
```

## Optical depth

```{r}

pdf('../analysis/Washington//Optical_depth/Mt.Wilson.boxplot.od.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot.od
dev.off()

pdf('../analysis/Washington//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../analysis/Washington//Optical_depth/Mt.Wilson.1905.1920.trans.pdf',
    width = 8, height = 5)
Mt.Wilson.1905.1920.trans
dev.off()

pdf('../analysis/Washington//Optical_depth/Mt.Wilson.1912.od.pdf',
    width = 8, height = 5)
Mt.Wilson.1912.od 
dev.off()

pdf('../analysis/Washington//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r}

pdf('../analysis/Washington//Angstrom_parameter/Mt.Wilson.alpha.1905.1920.pdf',
    width = 8, height = 5)
Mt.Wilson.alpha.19052.1903
dev.off()

pdf('../analysis/Washington//Angstrom_parameter/Mt.Wilson.1912.alpha.pdf',
    width = 8, height = 5)
Mt.Wilson.1912.alpha
dev.off()

pdf('../analysis/Washington//Angstrom_parameter/Mt.Wilson.boxplot.alpha.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot.alpha
dev.off()

pdf('../analysis/Washington//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../analysis/Washington//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
