---
title: "Bachelorarbeit: Calama"
author: "Patrick Bigler"
date: "2023-09-03"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

We read our R-script with all the packages we need.

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(recipes::fixed)
conflicts_prefer(yardstick::rmse)
```

## Read data

First, we read the data. After that, we rewrite the date in a proper US-way
by using lubridate::ymd(). Further, we add a new column which contains the
raw-number. Finally, we replace all -999 values with NA.

```{r}
Calama.1918.1920 <- read.delim("../../Data/Calama.txt")

Calama.1918.1920 <- Calama.1918.1920|>
  dplyr::mutate('Date' = lubridate::ymd(paste(Calama.1918.1920$year,
                                              Calama.1918.1920$month,
                                              Calama.1918.1920$day,
                                              sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Calama.1918.1920$Location)))|>   
  dplyr::select(-c('year', 'month', 'day'))

Calama.1918.1920 <- replace(Calama.1918.1920, Calama.1918.1920 == -999, NA)
```

# Data-quality

## Rename columns

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Calama, message=FALSE, error=FALSE, warning=FALSE}
Calama <- Calama.1918.1920|>
  dplyr::rename('lambda_349' = 'lambda1...m.', 'lambda_395' = 'lambda2...m.',
                'lambda_450' = 'lambda3...m.', 'lambda_499' = 'lambda4...m.',
                'lambda_621' = 'lambda5...m.','lambda_714' = 'lambda6...m.',
                'lambda_803' = 'lambda7...m.','lambda_977' = 'lambda8...m.',
                'lambda_1214' = 'lambda9...m.','lambda_1593' = 'lambda10...m.',
                'trans_349' = 'transmission1....100.', 'trans_395' = 'transmission2....100.',
                'trans_450' = 'transmission3....100.','trans_499' = 'transmission4....100.',
                'trans_621' = 'transmission5....100.','trans_714' = 'transmission6....100.',
                'trans_803' = 'transmission7....100.','trans_977' = 'transmission8....100.',
                'trans_1214' = 'transmission9....100.',
                'trans_1593' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date', starts_with('la'), starts_with('t')))
```

## Errors, slice if necessary and rebuild

Here, we create all our tables we need. We rename our columns, set new
levels, create pivot tables or merge some tables. Further, we make some
quality-control calls.

-   If any value in the data set greater than 2, then it must be a error
    (because the wavelengths $\lambda\in[0.3, 1.6]$ and the transmission T
    is $T \in[0, 1]$).

<!-- -->

-   If a transmission value greater than 1, the it is impossible and we
    replace the value with NA.

-   If a transmission value smaller than 0.1, then it is possible but
    unlikely and we replace the value with NA.

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Transmission (long format)
################################################################################
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Calama <- Calama|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))

################################################################################
Calama_long <- Calama|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('349', '395', '450', '499', '621', 
                                 '714','803', '977', '1214', '1593'), times = 578))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_349", "trans_395", "trans_450", 
                           "trans_499", "trans_621", "trans_714", "trans_803",
                           "trans_977", "trans_1214", "trans_1593")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))

################################################################################
prep.mean <- Calama|>
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date, 
                   '349' = mean(trans_349, na.rm = TRUE),                   
                   '395' = mean(trans_395, na.rm = TRUE),                  
                   '450' = mean(trans_450, na.rm = TRUE),                   
                   '499' = mean(trans_499, na.rm = TRUE),                   
                   '621' = mean(trans_621, na.rm = TRUE),                   
                   '714' = mean(trans_714, na.rm = TRUE),   
                   '803' = mean(trans_803, na.rm = TRUE), 
                   '977' = mean(trans_977, na.rm = TRUE),                   
                   '1214' = mean(trans_1214, na.rm = TRUE),
                   '1593' = mean(trans_1593, na.rm = TRUE))|>
  pivot_longer(cols = -c('month', 'Date'), 
               names_to = 'variable', values_to = 'value')

prep.std <- Calama|>
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date,
                   'std_349' = sd(trans_349, na.rm = TRUE),                   
                   'std_395' = sd(trans_395, na.rm = TRUE),                  
                   'std_450' = sd(trans_450, na.rm = TRUE),                   
                   'std_499' = sd(trans_499, na.rm = TRUE),                   
                   'std_621' = sd(trans_621, na.rm = TRUE),                   
                   'std_714' = sd(trans_714, na.rm = TRUE),   
                   'std_803' = sd(trans_803, na.rm = TRUE), 
                   'std_977' = sd(trans_977, na.rm = TRUE),                   
                   'std_1214' = sd(trans_1214, na.rm = TRUE),
                   'std_1593' = sd(trans_1593, na.rm = TRUE)) |>
  pivot_longer(cols = -c('month', 'Date'), 
               names_to = 'variable', values_to = 'value')

transmission <- inner_join(prep.mean, prep.std, by = 'Date') |>
  dplyr::rename('month' = 'month.x',
                'variable' = 'variable.x',
                'mean' = 'value.x',
                'std' = 'value.y')|>
  dplyr::select(c('month', 'variable', 'mean', 'std'))|>
  group_by(month, variable)|>
  dplyr::summarise(mean = mean(mean),
                   std = mean(std))|>
  dplyr::mutate(variable = factor(variable,
                levels = c('349', '395', '450', '499', '621', 
                                 '714','803', '977', '1214', '1593'))) |>
  dplyr::filter(variable == '349' | variable == '395' | variable == '450' |
                  variable == '621' | variable == '1593')

################################################################################
trans_annual_mean <- Calama|>
  dplyr::select(c('row','Date', starts_with('t'))) |>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise(Date = Date, 
                   '349' = mean(trans_349, na.rm = TRUE),                   
                   '395' = mean(trans_395, na.rm = TRUE),                  
                   '450' = mean(trans_450, na.rm = TRUE),                   
                   '499' = mean(trans_499, na.rm = TRUE),                   
                   '621' = mean(trans_621, na.rm = TRUE),                   
                   '714' = mean(trans_714, na.rm = TRUE),   
                   '803' = mean(trans_803, na.rm = TRUE), 
                   '977' = mean(trans_977, na.rm = TRUE),                   
                   '1214' = mean(trans_1214, na.rm = TRUE),
                   '1593' = mean(trans_1593, na.rm = TRUE))|>
  pivot_longer(cols = -c('month', 'Date'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c('349', '395', '450', '499', '621', 
                                 '714','803', '977', '1214', '1593')))

################################################################################
# Optical Depth
################################################################################
Calama_od <- Calama_long|>
  dplyr::mutate_at(c('values'), ~-log(.))

################################################################################
prep.mean.od <- Calama|>
  dplyr::mutate_at(c("trans_349", "trans_395", "trans_450", 
                           "trans_499", "trans_621", "trans_714", "trans_803",
                           "trans_977", "trans_1214", "trans_1593"), ~-log(.)) |>    
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date, 
                   '349' = mean(trans_349, na.rm = TRUE),                   
                   '395' = mean(trans_395, na.rm = TRUE),                  
                   '450' = mean(trans_450, na.rm = TRUE),                   
                   '499' = mean(trans_499, na.rm = TRUE),                   
                   '621' = mean(trans_621, na.rm = TRUE),                   
                   '714' = mean(trans_714, na.rm = TRUE),   
                   '803' = mean(trans_803, na.rm = TRUE), 
                   '977' = mean(trans_977, na.rm = TRUE),                   
                   '1214' = mean(trans_1214, na.rm = TRUE),
                   '1593' = mean(trans_1593, na.rm = TRUE))|>
  pivot_longer(cols = -c('month', 'Date'), 
               names_to = 'variable', values_to = 'value')

prep.std.od <- Calama|>
  dplyr::mutate_at(c("trans_349", "trans_395", "trans_450", 
                           "trans_499", "trans_621", "trans_714", "trans_803",
                           "trans_977", "trans_1214", "trans_1593"), ~-log(.)) |>  
  group_by(month = lubridate::month(Date, label = TRUE))|>
  dplyr::summarise(Date = Date,
                   'std_349' = sd(trans_349, na.rm = TRUE),                   
                   'std_395' = sd(trans_395, na.rm = TRUE),                  
                   'std_450' = sd(trans_450, na.rm = TRUE),                   
                   'std_499' = sd(trans_499, na.rm = TRUE),                   
                   'std_621' = sd(trans_621, na.rm = TRUE),                   
                   'std_714' = sd(trans_714, na.rm = TRUE),   
                   'std_803' = sd(trans_803, na.rm = TRUE), 
                   'std_977' = sd(trans_977, na.rm = TRUE),                   
                   'std_1214' = sd(trans_1214, na.rm = TRUE),
                   'std_1593' = sd(trans_1593, na.rm = TRUE))|>
  dplyr::select(c('Date','month', starts_with('std'))) |>
  pivot_longer(cols = starts_with(c('std')), 
               names_to = 'variable', values_to = 'value')

optical_depth <- inner_join(prep.mean.od, prep.std.od, by = 'Date') |>
  dplyr::rename('month' = 'month.x',
                'variable' = 'variable.x',
                'mean' = 'value.x',
                'std' = 'value.y')|>
  dplyr::select(c('month', 'variable', 'mean', 'std'))|>
  group_by(month, variable)|>
  dplyr::summarise(mean = mean(mean),
                   std = mean(std))|>
  dplyr::mutate(variable = factor(variable,
                levels = c('349', '395', '450', '499', '621', 
                                 '714','803', '977', '1214', '1593'))) |>
  dplyr::filter(variable == '349' | variable == '450' |
                  variable == '621' | variable == '1593')

################################################################################
od_annual_mean <- Calama|>
  dplyr::select(c('row','Date', starts_with('t'))) |>
  dplyr::mutate_at(c("trans_349", "trans_395", "trans_450", 
                           "trans_499", "trans_621", "trans_714", "trans_803",
                           "trans_977", "trans_1214", "trans_1593"), ~-log(.)) |>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise('349' = mean(trans_349, na.rm = TRUE),
                   '395' = mean(trans_395, na.rm = TRUE),
                   '450' = mean(trans_450, na.rm = TRUE),
                   '499' = mean(trans_499, na.rm = TRUE),
                   '621' = mean(trans_621, na.rm = TRUE),
                   '714' = mean(trans_714, na.rm = TRUE),
                   '803' = mean(trans_803, na.rm = TRUE),
                   '977' = mean(trans_977, na.rm = TRUE),
                   '1214' = mean(trans_1214, na.rm = TRUE),
                   '1593' = mean(trans_1593, na.rm = TRUE))|>
  pivot_longer(cols = -c('month'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c('349', '395', '450', '499', '621', 
                                 '714','803', '977', '1214', '1593')))

################################################################################
# Ågström parameter
################################################################################
Calama.alpha <- Calama|>
  dplyr::mutate(
    alpha_349 = -(log(Calama$trans_349) - log(Calama$trans_977)) / log(349),
    alpha_395 = -(log(Calama$trans_395) - log(Calama$trans_977)) / log(395),
    alpha_450 = -(log(Calama$trans_450) - log(Calama$trans_977)) / log(450),
    alpha_499 = -(log(Calama$trans_499) - log(Calama$trans_977)) / log(499),
    alpha_621 = -(log(Calama$trans_621) - log(Calama$trans_977)) / log(621),
    alpha_714 = -(log(Calama$trans_714) - log(Calama$trans_977)) / log(714),
    alpha_803 = -(log(Calama$trans_803) - log(Calama$trans_977)) / log(803),
    alpha_1214 = -(log(Calama$trans_1214) - log(Calama$trans_977)) / log(1214),
    alpha_1593 = -(log(Calama$trans_1593) - log(Calama$trans_977)) / log(1593)) |>
  dplyr::select(c('row','Date', starts_with('a')))

################################################################################
Calama.alpha.long <- Calama.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_349", "alpha_395", "alpha_450", 
                           "alpha_499", "alpha_621", "alpha_714", "alpha_803",
                           "alpha_1214", "alpha_1593")))

################################################################################
alpha_annual_mean <- Calama.alpha|>
  group_by(month = lubridate::floor_date(Date, 'year'))|>
  dplyr::summarise('349' = mean(alpha_349, na.rm = TRUE),
                   '395' = mean(alpha_395, na.rm = TRUE),
                   '450' = mean(alpha_450, na.rm = TRUE),
                   '499' = mean(alpha_499, na.rm = TRUE),
                   '621' = mean(alpha_621, na.rm = TRUE),
                   '714' = mean(alpha_714, na.rm = TRUE),
                   '803' = mean(alpha_803, na.rm = TRUE),
                   '1214' = mean(alpha_1214, na.rm = TRUE),
                   '1593' = mean(alpha_1593, na.rm = TRUE))|>
  pivot_longer(cols = -c('month'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c('349', '395', '450', '499', '621', 
                                 '714','803', '1214', '1593')))
```

# Graphs

In this section, the actual analysis is performed. For this purpose,
multiple graphs are created. First for the transmission, then for the
atmospheric optical depth and finally for the Ångström parameter.

## Transmission

### Overview transmission

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1918 - 1920)
Calama.1918.1920.trans <- Calama_long|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +  
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90) +  
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.1918.1920.trans

################################################################################
# Zoom in (year 1919)
Calama.1919.trans <- Calama_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k = 5, fill = NA, align = 'center')) |>
ggplot()+
  #geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90) + 
  labs(x = 'Time [months]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.1919.trans
```

### Boxplot

Be careful: Katla eruption in 1918!

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}
Calama.boxplot <- Calama_long|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.boxplot
```

### Monthly aggregated atmospheric transmission

```{r Transmission_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}
transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - std, ymax = mean + std), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [months]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r Annual_transmission, message=FALSE, warning=FALSE, error=FALSE}
annual_transmission <- trans_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0.3, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0.3, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [1918 - 1920]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(.3, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1918 - 1920)
Calama.1918.1920.od <- Calama_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  #dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

Calama.1918.1920.od

################################################################################
# Zoom in (year 1919)
Calama.1919.od <- Calama_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = .85, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [years]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))    

Calama.1919.od 
```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Calama.boxplot.od <- Calama_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
    #dplyr::filter(variable  != 'trans_900') |>  
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.boxplot.od
```

### Monthly aggregated optical depth

```{r monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - std, ymax = mean + std), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [months]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
annual_od <- od_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 1, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 1, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [1918 - 1920]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1918 - 1920)
Calama.alpha.1918.1920 <- Calama.alpha.long|>
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = -.1, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = -.1, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Date [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  scale_y_continuous(limits = c(-.1, .1)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.alpha.1918.1920

################################################################################
# Zoom in (year 1919)

Calama.1919.alpha <- Calama.alpha.long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31')) |>
  #dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.3) +
  labs(x = 'Time [months]', y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  scale_y_continuous(limits = c(-.01, .1)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.1919.alpha
```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Calama.boxplot.alpha <- Calama.alpha.long|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'black') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Calama.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
angstrom_overview <- Calama.alpha.long|>
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31'))|>
  #dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [months]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +  
  scale_y_continuous(limits = c(-.05, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = .2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = .2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [1918 - 1920]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(-.05, .2)) +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Calama//Transmission/Calama.1918.1920.trans.pdf',
    width = 8, height = 5)
Calama.1918.1920.trans
dev.off()

pdf('../../analysis/Calama//Transmission/Calama.1919.trans.pdf',
    width = 8, height = 5)
Calama.1919.trans
dev.off()

pdf('../../analysis/Calama//Transmission/Calama.boxplot.pdf',
    width = 8, height = 5)
Calama.boxplot
dev.off()

pdf('../../analysis/Calama//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Calama//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Calama//Optical_depth/Calama.1918.1920.od.pdf',
    width = 8, height = 5)
Calama.1918.1920.od
dev.off()

pdf('../../analysis/Calama//Optical_depth/Calama.1919.od.pdf',
    width = 8, height = 5)
Calama.1919.od 
dev.off()

pdf('../../analysis/Calama//Optical_depth/Calama.boxplot.od.pdf',
    width = 8, height = 5)
Calama.boxplot.od
dev.off()

pdf('../../analysis/Calama//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Calama//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Calama//Angstrom_parameter/Calama.alpha.1918.1920.pdf',
    width = 8, height = 5)
Calama.alpha.1918.1920
dev.off()

pdf('../../analysis/Calama//Angstrom_parameter/Calama.1919.alpha.pdf',
    width = 8, height = 5)
Calama.1919.alpha
dev.off()

pdf('../../analysis/Calama//Angstrom_parameter/Calama.boxplot.alpha.pdf',
    width = 8, height = 5)
Calama.boxplot.alpha
dev.off()

pdf('../../analysis/Calama//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../../analysis/Calama//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
