---
title: "Bachelorarbeit: Haraqua_Hala"
author: "Patrick Bigler"
date: "2023-09-03"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

+-----------------------+-------------------------------------------------+
| **Project:**          | **Bachelor thesis**                             |
+=======================+=================================================+
| **Title:**            | **Extracting Signals of Volcanic Events from    |
|                       | Transmission data measured by**                 |
|                       |                                                 |
|                       | **the Smithsonian Institution between 1902 and  |
|                       | 1930**                                          |
+-----------------------+-------------------------------------------------+
| **Author:**           | **Patrick Bigler                                |
|                       | (patrick.bigler1\@stundents.unibe.ch**          |
+-----------------------+-------------------------------------------------+
| -   \*Supervisor:\*\* | **Prof. Dr. Stefan Brönnimann                   |
|                       | (stefan.brönnimann\@unibe.ch)**                 |
+-----------------------+-------------------------------------------------+
| **Institution:**      | **University of Bern, Institute of Geography,   |
|                       | Unit Climatology**                              |
+-----------------------+-------------------------------------------------+

# Introduction

## Read packages

We read our R-script with all the packages we need.

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(recipes::fixed)
conflicts_prefer(yardstick::rmse)
conflicts_prefer(ggplot2::vars)
```

## Read data

First, we read the data. After that, we rewrite the date in a proper US-way
by using lubridate::ymd(). Further, we add a new column which contains the
raw-number. Finally, we replace all -999 values with NA.

```{r Read_data, message=FALSE, error=FALSE, warning=FALSE}
Harqua_Hala.1920.1925 <- read.delim("../../Data/Harqua_Hala.txt")

Harqua_Hala.1920.1925 <- Harqua_Hala.1920.1925|>
  dplyr::mutate('Date' = lubridate::ymd(paste(Harqua_Hala.1920.1925$year,
                                              Harqua_Hala.1920.1925$month,
                                              Harqua_Hala.1920.1925$day,
                                              sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Harqua_Hala.1920.1925$Location)))|>  
  dplyr::select(-c('year', 'month', 'day'))  

Harqua_Hala.1920.1925 <- replace(Harqua_Hala.1920.1925, Harqua_Hala.1920.1925 == -999, NA)

write_csv(Harqua_Hala.1920.1925, '../../data/trans_Timeline/Haraqua_Hala.ok.csv')
```

# Data-quality

## Rename columns

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Haraqua_Hala, message=FALSE, error=FALSE, warning=FALSE}
Haraqua_Hala <- Harqua_Hala.1920.1925|>
  dplyr::rename('lambda_350' = 'lambda1...m.', 'lambda_398' = 'lambda2...m.',
                'lambda_452' = 'lambda3...m.', 'lambda_502' = 'lambda4...m.',
                'lambda_626' = 'lambda5...m.','lambda_724' = 'lambda6...m.',
                'lambda_817' = 'lambda7...m.','lambda_994' = 'lambda8...m.',
                'lambda_1225' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_350' = 'transmission1....100.', 'trans_398' = 'transmission2....100.',
                'trans_452' = 'transmission3....100.','trans_502' = 'transmission4....100.',
                'trans_626' = 'transmission5....100.','trans_724' = 'transmission6....100.',
                'trans_817' = 'transmission7....100.','trans_994' = 'transmission8....100.',
                'trans_1225' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date', starts_with('la'), starts_with('t')))
```

## Errors, slice if necessary and rebuild

Here, we create all our tables we need. We rename our columns, set new
levels, create pivot tables or merge some tables. Further, we make some
quality-control calls.

-   If any value in the data set greater than 2, then it must be a error
    (because the wavelengths $\lambda\in[0.3, 1.6]$ and the transmission T
    is $T \in[0, 1]$).
-   If a transmission value greater than 1, the it is impossible and we
    replace the value with NA.
-   If a transmission value smaller than 0.1, then it is possible but
    unlikely and we replace the value with NA.

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Haraqua_Hala <- Haraqua_Hala|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))
################################################################################
# Transmission (long format)
################################################################################
Haraqua_Hala_long <- Haraqua_Hala|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('350', '398', '452', '502', '626', 
                                 '724','817', '994', '1225', '1600'), times = 226))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_398", "trans_452", 
                           "trans_502", "trans_626", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))
################################################################################
transmission <- Haraqua_Hala_long|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_398' | variable == 'trans_452' 
                | variable == 'trans_626' |variable == 'trans_724'| variable == 'trans_1600')
################################################################################
trans_annual_mean <- Haraqua_Hala_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_398", "trans_452", 
                           "trans_502", "trans_626", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

################################################################################
# Optical Depth
################################################################################
Haraqua_Hala_od <- Haraqua_Hala_long|>
  dplyr::mutate_at(c('values'), ~-log(.))
################################################################################
optical_depth <- Haraqua_Hala_od|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    dplyr::filter(Date < as_date('1924-01-01')) |>
    dplyr::filter(lubridate::month(Date) == 5| lubridate::month(Date) == 6| lubridate::month(Date) == 7| 
                lubridate::month(Date) == 8 | lubridate::month(Date) == 9 |lubridate::month(Date) == 10 |
                  lubridate::month(Date) == 11) |>
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_398' | variable == 'trans_452' 
                | variable == 'trans_626' |variable == 'trans_724'| variable == 'trans_1600')

stats <- Haraqua_Hala_od|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    dplyr::filter(Date < as_date('1924-01-01')) |>
    dplyr::filter(lubridate::month(Date) == 5| lubridate::month(Date) == 6| lubridate::month(Date) == 7| 
                lubridate::month(Date) == 8 | lubridate::month(Date) == 9 |lubridate::month(Date) == 10 |
                  lubridate::month(Date) == 11) |>
    group_by(variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))

stats |>
  mutate(percent = 100*(`sd`+`mean`)/`mean`)

################################################################################
od_annual_mean <- Haraqua_Hala_od|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_398", "trans_452", 
                           "trans_502", "trans_626", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(od_annual_mean, '../../data/od_Timeline/Haraqua_Hala.od.csv')
################################################################################
# Ågström parameter
################################################################################
Haraqua_Hala.alpha <- Haraqua_Hala|>
  dplyr::mutate(
    alpha_350 = -(log(Haraqua_Hala$trans_350) - log(Haraqua_Hala$trans_994)) / log(350),
    alpha_400 = -(log(Haraqua_Hala$trans_398) - log(Haraqua_Hala$trans_994)) / log(398),
    alpha_450 = -(log(Haraqua_Hala$trans_452) - log(Haraqua_Hala$trans_994)) / log(452),
    alpha_500 = -(log(Haraqua_Hala$trans_502) - log(Haraqua_Hala$trans_994)) / log(502),
    alpha_600 = -(log(Haraqua_Hala$trans_626) - log(Haraqua_Hala$trans_994)) / log(626),
    alpha_700 = -(log(Haraqua_Hala$trans_724) - log(Haraqua_Hala$trans_994)) / log(724),
    alpha_800 = -(log(Haraqua_Hala$trans_817) - log(Haraqua_Hala$trans_994)) / log(817),
    alpha_900 = NA,
    alpha_1200 = -(log(Haraqua_Hala$trans_1225) - log(Haraqua_Hala$trans_994)) / log(1225),
    alpha_1600 = -(log(Haraqua_Hala$trans_1600) - log(Haraqua_Hala$trans_994)) / log(1600)) |>
  dplyr::select(c('row','Date', starts_with('a')))

################################################################################
Haraqua_Hala.alpha.long <- Haraqua_Hala.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", 
                           "alpha_500", "alpha_600", "alpha_700", "alpha_800",
                           'alpha_900',"alpha_1220", "alpha_1600")))

################################################################################

alpha_annual_mean <- Haraqua_Hala.alpha.long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", 
                           "alpha_500", "alpha_600", "alpha_700", "alpha_800",
                           'alpha_900',"alpha_1220", "alpha_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(alpha_annual_mean, '../../data/alpha_timeline/Haraqua_Hala.alpha.csv')
```

# Graphs

In this section, the actual analysis is performed. For this purpose,
multiple graphs are created. First for the transmission, then for the
atmospheric optical depth and finally for the Ångström parameter.

## Transmission

### Overview transmission

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1920 - 1925)
Haraqua_Hala.1920.1925.trans <- Haraqua_Hala_long|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = 0, label= "Raikoke [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = 0, label= "Raikoke [1924-02-15]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350','398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.1920.1925.trans

################################################################################
# Zoom in (year 1925)
Haraqua_Hala.1924.trans <- Haraqua_Hala_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1924-01-01') & Date < as_date('1926-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k = 5, fill = NA, align = 'center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = 0.2, label= "Raikoke [1924-02-15]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350','398','452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  scale_y_continuous(limits = c(0.2, 1)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))  

Haraqua_Hala.1924.trans
```

### Boxplot

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}
Haraqua_Hala.boxplot <- Haraqua_Hala_long|>
  dplyr::filter((Date > as_date('1920-01-01') & Date < as_date('1924-01-01')))|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.boxplot
```

### Monthly aggregated atmospheric transmission

```{r Transmission_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}
transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
  label = c('350','398' ,'452', '626','724' ,'1600')) +
  labs(x = 'Time [month]', y = 'Monthly aggregated transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r Annual_transmission, message=FALSE, warning=FALSE, error=FALSE}
annual_transmission <- trans_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = .3, label= "Raikoke [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = .3, label= "Raikoke [1924-02-15]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(.3, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1920 - 1925)
Haraqua_Hala.1920.1925.od <- Haraqua_Hala_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  #dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = 0, label= "Raikoke [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = 0, label= "Raikoke [1924-02-15]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  +
  theme(text = element_text(size = 20))    

Haraqua_Hala.1920.1925.od

################################################################################
# Zoom in (year 1924)
Haraqua_Hala.1924.od <- Haraqua_Hala_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(Date > as_date('1924-01-01') & Date < as_date('1924-11-30')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = 1.2, label= "Raikoke [1924-02-15]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [month]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b") +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.1924.od 


```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Haraqua_Hala.boxplot.od <- Haraqua_Hala_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.boxplot.od
```

### Monthly aggregated optical depth

```{r monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
  label = c('350','398' ,'452', '626','724' ,'1600')) +
  labs(x = 'Time [month]', y = 'Monthly aggregated optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
annual_od <- od_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = 1, label= "Raikoke [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = 1, label= "Raikoke [1924-02-15]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817','994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1920 - 1925)
Haraqua_Hala.alpha.1920.1925 <- Haraqua_Hala.alpha.long|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [year]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Date [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817', '1225', '1600')) +
  scale_y_continuous(limits = c(-.01, .2)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.alpha.1920.1925

################################################################################
# Zoom in (year 1924)

Haraqua_Hala.1924.alpha <- Haraqua_Hala.alpha.long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1924-01-01') & Date < as_date('1924-12-31')) |>
  #dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [1924-02-15]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [month]', y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817', '1225', '1600')) +
  scale_y_continuous(limits = c(-.01, .2)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.1924.alpha
```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Haraqua_Hala.boxplot.alpha <- Haraqua_Hala.alpha.long|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350' ,'398', '452', '502', '626', '724', 
                                 '817', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

Haraqua_Hala.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
angstrom_overview <- Haraqua_Hala.alpha.long|>
  dplyr::filter(Date > as_date('1924-01-01') & Date < as_date('1924-12-31'))|>
  #dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [1924-02-15]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('350' ,'398', '452', '502', '626', '724', 
                                 '817', '1225', '1600')) +  
  scale_y_continuous(limits = c(-.005, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))    

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1924-11-24", format = '%Y-%m-%d'), 
                xmax = as.Date("1925-05-26", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1925-05-26", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  geom_vline(xintercept = as.numeric(as.Date("1924-02-15")), linetype = 'dotted') +
  annotate("text", x = as.Date("1924-02-15", format = '%Y-%m-%d'),
  y = .2, label= "Raikoke [1924-02-15]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(-.01, .2)) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1), title = "Wavelength [nm]"),
                       label = c('350' ,'398', '452', '502', '626', '724', 
                                 '817', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))+
  theme(text = element_text(size = 20))     


annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Haraqua_Hala//Transmission/Haraqua_Hala.1920.1925.trans.pdf',
    width = 8, height = 5)
Haraqua_Hala.1920.1925.trans
dev.off()

pdf('../../analysis/Haraqua_Hala//Transmission/Haraqua_Hala.1924.trans.pdf',
    width = 8, height = 5)
Haraqua_Hala.1924.trans
dev.off()

pdf('../../analysis/Haraqua_Hala//Transmission/Haraqua_Hala.boxplot.pdf',
    width = 8, height = 5)
Haraqua_Hala.boxplot
dev.off()

pdf('../../analysis/Haraqua_Hala//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Haraqua_Hala//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Haraqua_Hala//Optical_depth/Haraqua_Hala.1920.1925.od.pdf',
    width = 8, height = 5)
Haraqua_Hala.1920.1925.od
dev.off()

pdf('../../analysis/Haraqua_Hala//Optical_depth/Haraqua_Hala.1924.od.pdf',
    width = 8, height = 5)
Haraqua_Hala.1924.od 
dev.off()

pdf('../../analysis/Haraqua_Hala//Optical_depth/Haraqua_Hala.boxplot.od.pdf',
    width = 8, height = 5)
Haraqua_Hala.boxplot.od
dev.off()

pdf('../../analysis/Haraqua_Hala//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Haraqua_Hala//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Haraqua_Hala//Angstrom_parameter/Haraqua_Hala.alpha.1920.1925.pdf',
    width = 8, height = 5)
Haraqua_Hala.alpha.1920.1925
dev.off()

pdf('../../analysis/Haraqua_Hala//Angstrom_parameter/Haraqua_Hala.1924.alpha.pdf',
    width = 8, height = 5)
Haraqua_Hala.1924.alpha
dev.off()

pdf('../../analysis/Haraqua_Hala//Angstrom_parameter/Haraqua_Hala.boxplot.alpha.pdf',
    width = 8, height = 5)
Haraqua_Hala.boxplot.alpha
dev.off()

pdf('../../analysis/Haraqua_Hala//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../../analysis/Haraqua_Hala//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
