---
title: "Bachelorarbeit: Hump_Mountain"
author: "Patrick Bigler"
date: "2023-09-03"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

+----------------+--------------------------------------------------------+
| **Project:**   | **Bachelor thesis**                                    |
+================+========================================================+
| **Title:**     | **Extracting Signals of Volcanic Events from           |
|                | Transmission data measured by**                        |
|                |                                                        |
|                | **the Smithsonian Institution between 1902 and 1930**  |
+----------------+--------------------------------------------------------+
| **Author:**    | **Patrick Bigler                                       |
|                | (patrick.bigler1\@stundents.unibe.ch**                 |
+----------------+--------------------------------------------------------+
| *              | **Prof. Dr. Stefan Brönnimann                          |
| *Supervisor:** | (stefan.brönnimann\@unibe.ch)**                        |
+----------------+--------------------------------------------------------+
| **             | **University of Bern, Institute of Geography, Unit     |
| Institution:** | Climatology**                                          |
+----------------+--------------------------------------------------------+

# Introduction

## Read packages

We read our R-script with all the packages we need.

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(recipes::fixed)
conflicts_prefer(yardstick::rmse)
```

## Read data

First, we read the data. After that, we rewrite the date in a proper US-way
by using lubridate::ymd(). Further, we add a new column which contains the
raw-number. Finally, we replace all -999 values with NA.

```{r Read_data, message=FALSE, error=FALSE, warning=FALSE}
Hump_Mountain.1917.1918 <- read.delim("../../Data/Hump_Mountain.txt")

Hump_Mountain.1917.1918 <- Hump_Mountain.1917.1918|>
  dplyr::mutate('Date' = lubridate::ymd(paste(Hump_Mountain.1917.1918$year,
                                              Hump_Mountain.1917.1918$month,
                                              Hump_Mountain.1917.1918$day,
                                              sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Hump_Mountain.1917.1918$Location)))|>  
  dplyr::select(-c('year', 'month', 'day'))

Hump_Mountain.1917.1918  <- replace(Hump_Mountain.1917.1918, 
                                    Hump_Mountain.1917.1918 == -999, NA)

write_csv(Hump_Mountain.1917.1918, '../../data/trans_Timeline/Hump_Mountain.ok.csv')
```

# Data-quality

## Rename columns

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Hump_Mountain, message=FALSE, error=FALSE, warning=FALSE}
Hump_Mountain <- Hump_Mountain.1917.1918|>
  dplyr::rename('lambda_400' = 'lambda1...m.', 'lambda_450' = 'lambda2...m.',
                'lambda_500' = 'lambda3...m.', 'lambda_600' = 'lambda4...m.',
                'lambda_700' = 'lambda5...m.','lambda_800' = 'lambda6...m.',
                'lambda_900' = 'lambda7...m.','lambda_1000' = 'lambda8...m.',
                'lambda_1200' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_400' = 'transmission1....100.', 'trans_450' = 'transmission2....100.',
                'trans_500' = 'transmission3....100.','trans_600' = 'transmission4....100.',
                'trans_700' = 'transmission5....100.','trans_800' = 'transmission6....100.',
                'trans_900' = 'transmission7....100.','trans_1000' = 'transmission8....100.',
                'trans_1200' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date', starts_with('la'), starts_with('t')))
```

## Errors, slice if necessary and rebuild

Here, we create all our tables we need. We rename our columns, set new
levels, create pivot tables or merge some tables. Further, we make some
quality-control calls.

-   If any value in the data set greater than 2, then it must be a error
    (because the wavelengths $\lambda\in[0.3, 1.6]$ and the transmission T
    is $T \in[0, 1]$).

<!-- -->

-   If a transmission value greater than 1, the it is impossible and we
    replace the value with NA.

-   If a transmission value smaller than 0.1, then it is possible but
    unlikely and we replace the value with NA.

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Hump_Mountain <- Hump_Mountain|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))

################################################################################
# Transmission (long format)
################################################################################
Hump_Mountain_long <- Hump_Mountain|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('400', '450', '500', '600', '700', 
                                 '800','900', '1000', '1200', '1600'), times = 58))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))
################################################################################
transmission <- Hump_Mountain_long|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_400' | variable == 'trans_450' | variable == 'trans_500' 
                | variable == 'trans_700' | variable == 'trans_1600')
################################################################################
trans_annual_mean <- Hump_Mountain_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))
################################################################################
# Optical Depth
################################################################################
Hump_Mountain_od <- Hump_Mountain_long|>
  dplyr::mutate_at(c('values'), ~-log(.))
################################################################################
optical_depth <- Hump_Mountain_od|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_400' | variable == 'trans_450' | variable == 'trans_500'
                | variable == 'trans_700' | variable == 'trans_1600')
################################################################################
od_annual_mean <- Hump_Mountain_od|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(od_annual_mean, '../../data/od_Timeline/Hump_Mountain.od.csv')
################################################################################
# Ågström parameter
################################################################################
Hump_Mountain.alpha <- Hump_Mountain|>
  dplyr::mutate(alpha_350 = NA,
    alpha_400 = -(log(Hump_Mountain$trans_400) - log(Hump_Mountain$trans_1000)) / log(349),
    alpha_450 = -(log(Hump_Mountain$trans_450) - log(Hump_Mountain$trans_1000)) / log(395),
    alpha_500 = -(log(Hump_Mountain$trans_500) - log(Hump_Mountain$trans_1000)) / log(450),
    alpha_600 = -(log(Hump_Mountain$trans_600) - log(Hump_Mountain$trans_1000)) / log(500),
    alpha_700 = -(log(Hump_Mountain$trans_700) - log(Hump_Mountain$trans_1000)) / log(621),
    alpha_800 = -(log(Hump_Mountain$trans_800) - log(Hump_Mountain$trans_1000)) / log(714),
    alpha_900 = -(log(Hump_Mountain$trans_900) - log(Hump_Mountain$trans_1000)) / log(803),
    alpha_1200 = -(log(Hump_Mountain$trans_1200) - log(Hump_Mountain$trans_1000)) / log(1214),
    alpha_1600 = -(log(Hump_Mountain$trans_1600) - log(Hump_Mountain$trans_1000)) / log(1593)) |>
  dplyr::select(c('row','Date', starts_with('a')))
################################################################################
Hump_Mountain.alpha.long <- Hump_Mountain.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c('alpha_350',"alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1200", "alpha_1600")))
################################################################################
alpha_annual_mean <- Hump_Mountain.alpha.long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c('alpha_350',"alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1200", "alpha_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(alpha_annual_mean, '../../data/alpha_timeline/Hump_Mountain.alpha.csv')
```

# Graphs

In this section, the actual analysis is performed. For this purpose,
multiple graphs are created. First for the transmission, then for the
atmospheric optical depth and finally for the Ångström parameter.

## Transmission

### Overview transmission

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1917 - 1918)
Hump_Mountain.1917.1918.trans <- Hump_Mountain_long|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Hump_Mountain.1917.1918.trans
```

### Boxplot

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}
Hump_Mountain.boxplot <- Hump_Mountain_long|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Hump_Mountain.boxplot
```

### Monthly aggregated atmospheric transmission

```{r Transmission_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}
transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
  label = c('355','403' ,'460', '637','1610')) +
  labs(x = 'Time [months]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r Annual_transmission, message=FALSE, warning=FALSE, error=FALSE}
annual_transmission <- trans_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  labs(x = 'Time [1920 - 1930]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(.3, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008','1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1917 - 1918)
Hump_Mountain.1917.1918.od <- Hump_Mountain_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

Hump_Mountain.1917.1918.od
```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Hump_Mountain.boxplot.od <- Hump_Mountain_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Hump_Mountain.boxplot.od
```

### Monthly aggregated optical depth

```{r monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
                       label = c('355', '460', '637','1610')) +
  labs(x = 'Time [months]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
annual_od <- od_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  labs(x = 'Time [1917 - 1918]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1008','1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1917 - 1918)
Hump_Mountain.alpha.1917.1918 <- Hump_Mountain.alpha.long|>
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Date [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  scale_y_continuous(limits = c(-.01, .1)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Hump_Mountain.alpha.1917.1918
```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Hump_Mountain.boxplot.alpha <- Hump_Mountain.alpha.long|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Hump_Mountain.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
angstrom_overview <- Hump_Mountain.alpha.long|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [months]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('355', '403', '460', '511', '637', 
                                 '702','830', '1244', '1610')) +  
  scale_y_continuous(limits = c(-.01, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  labs(x = 'Time [1917 - 1918]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(-.05, .2)) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1), title = "Wavelength [nm]"),
  label = c('355', '403', '460', '511', '637', 
                                 '702','830','1244', '1610')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Hump_Mountain//Transmission/Hump_Mountain.1917.1918.trans.pdf',
    width = 8, height = 5)
Hump_Mountain.1917.1918.trans
dev.off()

pdf('../../analysis/Hump_Mountain//Transmission/Hump_Mountain.boxplot.pdf',
    width = 8, height = 5)
Hump_Mountain.boxplot
dev.off()

pdf('../../analysis/Hump_Mountain//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Hump_Mountain//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Hump_Mountain//Optical_depth/Hump_Mountain.1917.1918.od.pdf',
    width = 8, height = 5)
Hump_Mountain.1917.1918.od
dev.off()

pdf('../../analysis/Hump_Mountain//Optical_depth/Hump_Mountain.boxplot.od.pdf',
    width = 8, height = 5)
Hump_Mountain.boxplot.od
dev.off()

pdf('../../analysis/Hump_Mountain//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Hump_Mountain//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Hump_Mountain//Angstrom_parameter/Hump_Mountain.alpha.1917.1918.pdf',
    width = 8, height = 5)
Hump_Mountain.alpha.1917.1918
dev.off()

pdf('../../analysis/Hump_Mountain//Angstrom_parameter/Hump_Mountain.boxplot.alpha.pdf',
    width = 8, height = 5)
Hump_Mountain.boxplot.alpha
dev.off()

pdf('../../analysis/Hump_Mountain//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../../analysis/Hump_Mountain//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
