---
title: "Bachelorarbeit: Mt. Wilson"
author: "Patrick Bigler"
date: "2023-07-07"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

We read our R-script with all the packages we need.

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(ggplot2::vars)
```

## Read data

First, we read the data. After that, we rewrite the date in a proper US-way
by using lubridate::ymd(). Further, we add a new column which contains the
raw-number. Finally, we replace all -999 values with NA.

```{r Read_data, message=FALSE, error=FALSE, warning=FALSE}
Mt.Wilson.1905.1920 <- read.delim("../../Data/Mt_Wilson_1.txt")

Mt.Wilson.1905.1906 <- read.delim("../../Data/Mt_Wilson_2.txt")

Mt.Wilson.1909.1912 <- read.delim("../../Data/Mt_Wilson_3.txt")


Mt.Wilson.1905.1920 <- Mt.Wilson.1905.1920|>
  dplyr::mutate('Date' = lubridate::ymd(paste(Mt.Wilson.1905.1920$year,
                                              Mt.Wilson.1905.1920$month,
                                              Mt.Wilson.1905.1920$day,
                                              sep = ' ')))|>
  dplyr::select(-c('year', 'month', 'day'))|>
  dplyr::mutate(row = seq(1 : length(Mt.Wilson.1905.1920$Location)))

Mt.Wilson.1905.1920 <- replace(Mt.Wilson.1905.1920, Mt.Wilson.1905.1920 == -999, NA)
```

# Data-quality

## Slice if necessary and rebuild

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Mt.Wilson, message=FALSE, error=FALSE, warning=FALSE}

Mt.Wilson_a <- Mt.Wilson.1905.1920|>
  slice(1:121)|>
  dplyr::rename('lambda_400' = 'lambda1...m.', 'lambda_450' = 'lambda2...m.',
                'lambda_500' = 'lambda3...m.', 'lambda_600' = 'lambda4...m.',
                'lambda_700' = 'lambda5...m.','lambda_800' = 'lambda6...m.',
                'lambda_900' = 'lambda7...m.','lambda_1000' = 'lambda8...m.',
                'lambda_1200' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_400' = 'transmission1....100.', 'trans_450' = 'transmission2....100.',
                'trans_500' = 'transmission3....100.','trans_600' = 'transmission4....100.',
                'trans_700' = 'transmission5....100.','trans_800' = 'transmission6....100.',
                'trans_900' = 'transmission7....100.','trans_1000' = 'transmission8....100.',
                'trans_1200' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::mutate('lambda_350' = 0.35, 'trans_350' = NA)|>
  dplyr::select(c('row', 'Date', starts_with('lambda_'), starts_with('trans_')))

Mt.Wilson_b <- Mt.Wilson.1905.1920|>
  slice(122:563)|>
    dplyr::rename('lambda_350' = 'lambda1...m.','lambda_400' = 'lambda2...m.',
                'lambda_450' = 'lambda3...m.','lambda_500' = 'lambda4...m.',
                'lambda_600' = 'lambda5...m.','lambda_700' = 'lambda6...m.',
                'lambda_800' = 'lambda7...m.', 'lambda_900' = 'lambda8...m.',
                'lambda_1000' = 'lambda9...m.', 'lambda_1200' = 'lambda10...m.',
                'lambda_1600' = 'lambda11...m.',
                'trans_350' = 'transmission1....100.','trans_400' = 'transmission2....100.',
                'trans_450' = 'transmission3....100.','trans_500' = 'transmission4....100.',
                'trans_600' = 'transmission5....100.','trans_700' = 'transmission6....100.',
                'trans_800' = 'transmission7....100.','trans_900' = 'transmission8....100.',
                'trans_1000' = 'transmission9....100.','trans_1200' = 'transmission10....100.',
                'trans_1600' = 'transmission11....100.')|>
    dplyr::select(c('row', 'Date', starts_with('lambda_'), starts_with('trans_')))

Mt.Wilson_c <- Mt.Wilson.1905.1920|>
  slice(564:1245)|>
  dplyr::rename('lambda_350' = 'lambda1...m.','lambda_400' = 'lambda2...m.',
                'lambda_450' = 'lambda3...m.','lambda_500' = 'lambda4...m.',
                'lambda_600' = 'lambda5...m.','lambda_700' = 'lambda6...m.',
                'lambda_800' = 'lambda7...m.','lambda_1000' = 'lambda8...m.',
                'lambda_1200' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_350' = 'transmission1....100.','trans_400' = 'transmission2....100.',
                'trans_450' = 'transmission3....100.', 'trans_500' = 'transmission4....100.',
                'trans_600' = 'transmission5....100.','trans_700' = 'transmission6....100.',
                'trans_800' = 'transmission7....100.','trans_1000' = 'transmission8....100.',
                'trans_1200' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.',)|>
  dplyr::mutate('lambda_900' = 0.9, 'trans_900' = NA)|>
  dplyr::select(c('row', 'Date', starts_with('lambda_'), starts_with('trans_')))

# We buil all back together
Mt.Wilson <- rbind(Mt.Wilson_a, Mt.Wilson_b)

Mt.Wilson <- rbind(Mt.Wilson, Mt.Wilson_c)

write_csv(Mt.Wilson, '../../data/trans_Timeline/Mt.Wilson.ok.csv')
```

## Errors

Here, we create all our tables we need. We rename our columns, set new
levels, create pivot tables or merge some tables. Further, we make some
quality-control calls.

-   If any value in the data set greater than 2, then it must be a error
    (because the wavelengths $\lambda\in[0.3, 1.6]$ and the transmission T
    is $T \in[0, 1]$).
-   If a transmission value greater than 1, the it is impossible and we
    replace the value with NA.
-   If a transmission value smaller than 0.1, then it is possible but
    unlikely and we replace the value with NA.

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Mt.Wilson <- Mt.Wilson|>
  dplyr::mutate(across(3:24, ~ifelse(.x > 2, NA, .x)))|>
  dplyr::filter(trans_1000 > 0.7)|>
  dplyr::filter(trans_1600 > 0.7)
################################################################################
# Transmission (long format)
################################################################################
Mt.Wilson_long <- Mt.Wilson|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('350', '400', '450', '500', '600', '700', 
                                 '800','900', '1000', '1200', '1600'), times = 1232))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))
################################################################################
transmission <- Mt.Wilson_long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01')))|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_400' | variable == 'trans_450' |
                  variable == 'trans_600' | variable == 'trans_700' 
                | variable == 'trans_1600')
	
(((0.9758991-0.013588493)/0.9758991)*100)-100

(((0.6021333-0.054709384)/0.6021333)*100)-100

################################################################################
trans_annual_mean <- Mt.Wilson_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    dplyr::filter(variable != 'trans_900') |>
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(trans_annual_mean, '../../data/od_Timeline/Mt.Wilson.od.csv')
################################################################################
# Optical Depth
################################################################################
Mt.Wilson_od <- Mt.Wilson_long|>
  dplyr::mutate_at(c('values'), ~-log(.))
################################################################################
optical_depth <- Mt.Wilson_od|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01')))|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_400' | variable == 'trans_450' |
                  variable == 'trans_600' | variable == 'trans_700' 
                | variable == 'trans_1600')
################################################################################
od_annual_mean <- Mt.Wilson_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    dplyr::filter(variable != 'trans_900') |>
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))
################################################################################
# Ågström parameter
################################################################################
Mt.Wilson.alpha <- Mt.Wilson|>
  dplyr::mutate(
    alpha_350 = -(log(Mt.Wilson$trans_350) - log(Mt.Wilson$trans_1000)) / log(350),
    alpha_400 = -(log(Mt.Wilson$trans_400) - log(Mt.Wilson$trans_1000)) / log(400),
    alpha_450 = -(log(Mt.Wilson$trans_450) - log(Mt.Wilson$trans_1000)) / log(450),
    alpha_500 = -(log(Mt.Wilson$trans_500) - log(Mt.Wilson$trans_1000)) / log(500),
    alpha_600 = -(log(Mt.Wilson$trans_600) - log(Mt.Wilson$trans_1000)) / log(600),
    alpha_700 = -(log(Mt.Wilson$trans_700) - log(Mt.Wilson$trans_1000)) / log(700),
    alpha_800 = -(log(Mt.Wilson$trans_800) - log(Mt.Wilson$trans_1000)) / log(800),
    alpha_900 = -(log(Mt.Wilson$trans_900) - log(Mt.Wilson$trans_1000)) / log(900),
    alpha_1200 = -(log(Mt.Wilson$trans_1200) - log(Mt.Wilson$trans_1000)) / log(1200),
    alpha_1600 = -(log(Mt.Wilson$trans_1600) - log(Mt.Wilson$trans_1000)) / log(1600)) |>
  dplyr::select(c('row','Date', starts_with('a')))
################################################################################
Mt.Wilson.alpha.long <- Mt.Wilson.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                          "alpha_1200", "alpha_1600")))
################################################################################
alpha_annual_mean <- Mt.Wilson.alpha.long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1000", "alpha_1200", "alpha_1600")))|> 
    dplyr::filter(variable != 'trans_900') |>
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write.csv(alpha_annual_mean, '../../data/alpha_timeline/Mt.Wilson.alpha.csv')
```

## Tables

```{r eval=FALSE}
kable(Mt.Wilson, align = c('l', rep('c', times = 23)))|>
  kable_styling()
```

### Transmissison

```{r eval=FALSE}
kable(Mt.Wilson_long, align = 'lccc')|>
  kable_styling()
```

```{r eval=FALSE}
kable(transmission, align = c('l', rep('c', times = 9)))|>
  kable_styling()   
```

```{r eval=FALSE}
kable(trans_annual_mean, align = 'lcc')|>
  kable_styling()
```

### Optical Depth

```{r eval=FALSE}
kable(Mt.Wilson_od , align = c('l', rep('c', times = 11)))|>
  kable_styling()
```

```{r eval=FALSE}
kable(optical_depth, align = c('l', rep('c', times = 9)))|>
  kable_styling()
```

```{r eval=FALSE}
kable(trans_annual_mean, align = 'lcc')|>
  kable_styling()
```

### Ångström Parameter

```{r eval=FALSE}
kable(Mt.Wilson.alpha, align = c('l', rep('c', times = 11)))|>
  kable_styling()
```

```{r eval=FALSE}
kable(Mt.Wilson.alpha.long, align = 'lccc')|>
  kable_styling()
```

```{r eval=FALSE}
kable(alpha_annual_mean, align = 'lcc')|>
  kable_styling()
```

# Graphs

## Transmission

### Overview transmission

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}

################################################################################
# Overview (1905 - 1920)

Mt.Wilson.1905.1920.trans <- Mt.Wilson_long|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 0, label= "Novarupta [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [1907-03-28]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0, label= "Katmai [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

################################################################################
# Zoom in (year 1908)
  
Mt.Wilson.1908.trans <- Mt.Wilson_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1908-01-01') & Date < as_date('1908-12-31')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable), cex.lab=1.5, cex.axis=1.5) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  scale_y_continuous(limits = c(0.2, 1)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))


################################################################################
# Zoom in (year 1912)
  
Mt.Wilson.1912.trans <- Mt.Wilson_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1912-01-01') & Date < as_date('1913-01-01')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  scale_y_continuous(limits = c(0.2, 1)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

################################################################################
# Zoom in (year 1919)
  
Mt.Wilson.1919.trans <- Mt.Wilson_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  scale_y_continuous(limits = c(0.2, 1)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Mt.Wilson.1905.1920.trans

Mt.Wilson.1908.trans

Mt.Wilson.1912.trans

Mt.Wilson.1919.trans
```

### Boxplot

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}

#function for theoretical calculation
source('../../R/General/theoretical_transmission.R')
# Create a sequenze with wavelenth between 0.1nm and 1.6nm
wavelenghts <- c(0.35, .4, .45, .5, .6, .7, .8, .9, 1, 1.2, 1.6)
# Create a sequenze with wavelengths and zenith angle
values <- transmittance(wavelenghts)
# Put all values in a tibble
theoretical.values <- tibble("lambda" = seq(from = 1, to = 11, by = 1),
                             'normal_irradiation' = values)

Mt.Wilson.boxplot <- Mt.Wilson_long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = as.factor(variable), y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = "deepskyblue") +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = 0, alpha = .1) +
  scale_x_discrete(labels = c(350, 400, 450, 500, 600, 700, 800, 
                              900,1000, 1200, 1600)) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Mt.Wilson.boxplot

###############################################################################################
# some statistics

Mt.Wilson.stat <- kable(Mt.Wilson_long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
  group_by(variable)|>
  summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE))), align = "lccccc", format = 'html',
  col.names = c("Variable", "Min", "Max", "Median","STD", "0.25-Quantil", "0.75-Quantil","IQR"))|>
  kable_styling()
Mt.Wilson.stat
```

### Monthly aggregated atmospheric transmission

```{r transmissio_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}

transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1), 
                       label = c('350', '400', '450', '600', '700', '1600'))) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r annual_transmission ,message=FALSE, warning=FALSE, error=FALSE}

annual_transmission <- trans_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 0, label= "Novarupta [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0, label= "Katla [NEEM-S1]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0, label= "Novarupta [1912-06-06]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 0, label= "Ksudach [1907-03-28]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0, label= "Katla [1918-10-12]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r  Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1905 - 1920)

Mt.Wilson.1905.1920.od <- Mt.Wilson_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +  
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) + 
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +  
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

################################################################################
# Zoom in (year 1908)
Mt.Wilson.1908.od <- Mt.Wilson_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(variable  != 'trans_900') |>    
  dplyr::filter(Date > as_date('1907-01-01') & Date < as_date('1908-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
 # geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  #annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  #y = 1.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +  
  labs(x = 'Time [month]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  scale_y_continuous(limits = c(0, 1.2)) +  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)) 

################################################################################
# Zoom in (year 1912)
Mt.Wilson.1912.od <- Mt.Wilson_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(variable  != 'trans_900') |>    
  dplyr::filter(Date > as_date('1912-01-01') & Date < as_date('1912-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +
  labs(x = 'Time [month]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

################################################################################
# Zoom in (year 1919)
Mt.Wilson.1919.od <- Mt.Wilson_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(variable  != 'trans_900') |>    
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  labs(x = 'Time [month]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  scale_y_continuous(limits = c(0, 1.2)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)) 

Mt.Wilson.1905.1920.od

Mt.Wilson.1908.od

Mt.Wilson.1912.od 

Mt.Wilson.1919.od
```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Mt.Wilson.boxplot.od <- Mt.Wilson_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
    dplyr::filter(variable  != 'trans_900') |>  
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'red', fill = 'deepskyblue' ) +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Mt.Wilson.boxplot.od
```

### Monthly aggregated optical depth

```{r  monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}

annual_od <- od_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 1.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 1.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 1.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1.2))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1905 - 1920)

Mt.Wilson.alpha.1905.1920 <- Mt.Wilson.alpha.long|>
  dplyr::filter(variable  != 'alpha_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = 0.2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = 0.2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +  
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = 0.2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novaruptu [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = 0.2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +  
  labs(x = 'Time [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Mt.Wilson.alpha.1905.1920

################################################################################
# Zoom in (year 1912)

Mt.Wilson.1912.alpha <- Mt.Wilson.alpha.long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1912-01-01') & Date < as_date('1913-01-01')) |>
  dplyr::filter(variable  != 'alpha_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = 0.2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +
  labs(x = 'Time [month]', y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350','400','450','500',
                                                     '600','700','800','1200','1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))


Mt.Wilson.1912.alpha

```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Mt.Wilson.boxplot.alpha <- Mt.Wilson.alpha.long|>
    dplyr::filter((Date > as_date('1909-01-01') & Date < as_date('1911-01-31')) |
                  (Date > as_date('1914-01-01') & Date < as_date('1918-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = .1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Mt.Wilson.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}

angstrom_overview.1908 <- Mt.Wilson.alpha.long|>
  dplyr::filter(Date > as_date('1908-01-01') & Date < as_date('1908-12-31')) |>
    dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('350','400','450','500',
                                                     '600','700','800','1200','1600')) +
  scale_y_continuous(limits = c(-.005, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview.1912 <- Mt.Wilson.alpha.long|>
  dplyr::filter(Date > as_date('1912-05-01') & Date < as_date('1913-01-01'))|>
    dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = .2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('350','400','450','500',
                                                     '600','700','800','1200','1600')) +
  scale_y_continuous(limits = c(-.005, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview.1919 <- Mt.Wilson.alpha.long|>
  dplyr::filter(Date > as_date('1919-01-01') & Date < as_date('1919-12-31')) |>
    dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('350','400','450','500',
                                                     '600','700','800','1200','1600')) +
  scale_y_continuous(limits = c(-.005, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview.1908 

angstrom_overview.1912

angstrom_overview.1919
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1908-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1909-08-09", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
            color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +   
  geom_rect(aes(xmin = as.Date("1912-06-12", format = '%Y-%m-%d'), 
                xmax = as.Date("1914-06-04", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  geom_rect(aes(xmin = as.Date("1918-01-01", format = '%Y-%m-%d'), 
                xmax = as.Date("1920-03-19", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1909-08-09", format = '%Y-%m-%d'),
  y = .2, label= "Ksudach [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1914-06-04", format = '%Y-%m-%d'),
  y = .2, label= "Novarupta [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1920-03-19", format = '%Y-%m-%d'),
  y = .2, label= "Katla [NEEM-S1]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1912-06-06")), linetype = 'dotted') +
  geom_vline(xintercept = as.numeric(as.Date("1907-03-28")), linetype = 'dotted') +  
  geom_vline(xintercept = as.numeric(as.Date("1918-10-12")), linetype = 'dotted') + 
  annotate("text", x = as.Date("1912-06-06", format = '%Y-%m-%d'),
  y = .2, label= "Novarupta [1912-06-06]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +
  annotate("text", x = as.Date("1907-03-28", format = '%Y-%m-%d'),
  y = .2, label= "Ksudach [1907-03-28]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +  
  annotate("text", x = as.Date("1918-10-12", format = '%Y-%m-%d'),
  y = .2, label= "Katla [1918-10-12]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  labs(x = 'Time [year]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(0, .2))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Mt.Wilson/Transmission/Mt.Wilson.1905.1920.trans.pdf',
        width = 8  , height = 5)
Mt.Wilson.1905.1920.trans
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/Mt.Wilson.1908.trans.pdf',
    width = 8  , height = 5)
Mt.Wilson.1908.trans
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/Mt.Wilson.1912.trans.pdf',
    width = 8  , height = 5)
Mt.Wilson.1912.trans
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/Mt.Wilson.1919.trans.pdf',
    width = 8  , height = 5)
Mt.Wilson.1919.trans
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/Mt.Wilson.boxplot.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Mt.Wilson/Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Mt.Wilson/Optical_depth/Mt.Wilson.1905.1920.od.pdf',
    width = 8, height = 5)
Mt.Wilson.1905.1920.od 
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/Mt.Wilson.1908.od .pdf',
    width = 8, height = 5)
Mt.Wilson.1908.od 
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/Mt.Wilson.1912.od.pdf',
    width = 8, height = 5)
Mt.Wilson.1912.od 
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/Mt.Wilson.1919.od.pdf',
    width = 8, height = 5)
Mt.Wilson.1919.od 
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/Mt.Wilson.boxplot.od.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot.od
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Mt.Wilson/Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Mt.Wilson/Angstrom_parameter/Mt.Wilson.alpha.1905.1920.pdf',
    width = 8, height = 5)
Mt.Wilson.alpha.1905.1920
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/Mt.Wilson.1912.alpha.pdf',
    width = 8, height = 5)
Mt.Wilson.1912.alpha
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/Mt.Wilson.boxplot.alpha.pdf',
    width = 8, height = 5)
Mt.Wilson.boxplot.alpha
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/angstrom_overview.1908.pdf',
    width = 8, height = 5)
angstrom_overview.1908
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/angstrom_overview.1912.pdf',
    width = 8, height = 5)
angstrom_overview.1912
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/angstrom_overview.1919.pdf',
    width = 8, height = 5)
angstrom_overview.1919
dev.off()

pdf('../../analysis/Mt.Wilson/Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
