---
title: "Bachelorarbeit: Table_Mountain"
author: "Patrick Bigler"
date: "2023-09-03"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

We read our R-script with all the packages we need.

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(recipes::fixed)
conflicts_prefer(yardstick::rmse)
```

## Read data

First, we read the data. After that, we rewrite the date in a proper US-way
by using lubridate::ymd(). Further, we add a new column which contains the
raw-number. Finally, we replace all -999 values with NA.

```{r}

Table_Mountain.1925.1930 <- read.delim("../../Data/Table_mountain.txt")

Table_Mountain.1925.1930 <- Table_Mountain.1925.1930|>
  dplyr::mutate('Date' = lubridate::ymd(paste(Table_Mountain.1925.1930$year,
                                              Table_Mountain.1925.1930$month,
                                              Table_Mountain.1925.1930$day,
                                              sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Table_Mountain.1925.1930$Location)))|>   
  dplyr::select(-c('year', 'month', 'day'))

Table_Mountain.1925.1930 <- replace(Table_Mountain.1925.1930, 
                                    Table_Mountain.1925.1930 == -999, NA)

write_csv(Table_Mountain.1925.1930, '../../data/trans_Timeline/Table_Mountain.ok.csv')
```

# Data-quality

## Rename columns

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Table_mountain, message=FALSE, error=FALSE, warning=FALSE}
Table_Mountain <- Table_Mountain.1925.1930 |>
  dplyr::rename('lambda_348' = 'lambda1...m.', 'lambda_391' = 'lambda2...m.',
                'lambda_446' = 'lambda3...m.', 'lambda_497' = 'lambda4...m.',
                'lambda_615' = 'lambda5...m.','lambda_724' = 'lambda6...m.',
                'lambda_817' = 'lambda7...m.','lambda_994' = 'lambda8...m.',
                'lambda_1225' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_348' = 'transmission1....100.', 'trans_391' = 'transmission2....100.',
                'trans_446' = 'transmission3....100.','trans_497' = 'transmission4....100.',
                'trans_615' = 'transmission5....100.','trans_724' = 'transmission6....100.',
                'trans_817' = 'transmission7....100.','trans_994' = 'transmission8....100.',
                'trans_1225' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date', starts_with('la'), starts_with('t')))
```

## Errors, slice if necessary and rebuild

Here, we create all our tables we need. We rename our columns, set new
levels, create pivot tables or merge some tables. Further, we make some
quality-control calls.

-   If any value in the data set greater than 2, then it must be a error
    (because the wavelengths $\lambda\in[0.3, 1.6]$ and the transmission T
    is $T \in[0, 1]$).
-   If a transmission value greater than 1, the it is impossible and we
    replace the value with NA.
-   If a transmission value smaller than 0.1, then it is possible but
    unlikely and we replace the value with NA.

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Table_Mountain <- Table_Mountain|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))
################################################################################
# Transmission (long format)
################################################################################
Table_Mountain_long <- Table_Mountain|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('348', '391', '446', '497' ,'615', 
                                 '724','817', '994', '1225', '1600'), times = 445))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_348", "trans_391", "trans_446", 
                           "trans_497", "trans_615", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))
################################################################################
transmission <- Table_Mountain_long|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_391' | variable == 'trans_446' | variable == 'trans_497' 
                | variable == 'trans_724' | variable == 'trans_1600')
################################################################################
trans_annual_mean <- Table_Mountain_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_348", "trans_391", "trans_446", 
                           "trans_497", "trans_615", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

################################################################################
# Optical Depth
################################################################################
Table_Mountain_od <- Table_Mountain_long|>
  dplyr::mutate_at(c('values'), ~-log(.))
################################################################################
optical_depth <- Table_Mountain_od|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_391' | variable == 'trans_446' | variable == 'trans_497' 
                | variable == 'trans_724' | variable == 'trans_1600')
################################################################################
od_annual_mean <- Table_Mountain_od|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_348", "trans_391", "trans_446", 
                           "trans_497", "trans_615", "trans_724", "trans_817",
                           "trans_994", "trans_1225", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(od_annual_mean, '../../data/od_Timeline/Table_Mountain.od.csv')
################################################################################
# Ågström parameter
################################################################################
Table_Mountain.alpha <- Table_Mountain|>
  dplyr::mutate(
    alpha_350 = -(log(Table_Mountain$trans_348) - log(Table_Mountain$trans_994)) / log(348),
    alpha_400 = -(log(Table_Mountain$trans_391) - log(Table_Mountain$trans_994)) / log(391),
    alpha_450 = -(log(Table_Mountain$trans_446) - log(Table_Mountain$trans_994)) / log(446),
    alpha_500 = -(log(Table_Mountain$trans_497) - log(Table_Mountain$trans_994)) / log(497),
    alpha_600 = -(log(Table_Mountain$trans_615) - log(Table_Mountain$trans_994)) / log(615),
    alpha_700 = -(log(Table_Mountain$trans_724) - log(Table_Mountain$trans_994)) / log(724),
    alpha_800 = -(log(Table_Mountain$trans_817) - log(Table_Mountain$trans_994)) / log(817),
    alpha_900 = NA,
    alpha_1200 = -(log(Table_Mountain$trans_1225) - log(Table_Mountain$trans_994)) / log(1225),
    alpha_1600 = -(log(Table_Mountain$trans_1600) - log(Table_Mountain$trans_994)) / log(1600)) |>
  dplyr::select(c('row','Date', starts_with('a')))

################################################################################
Table_Mountain.alpha.long <- Table_Mountain.alpha|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", 
                           "alpha_500", "alpha_600", "alpha_700", "alpha_800",
                           'alpha_900',"alpha_1220", "alpha_1600")))

################################################################################

alpha_annual_mean <- Table_Mountain.alpha.long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", 
                           "alpha_500", "alpha_600", "alpha_700", "alpha_800",
                           'alpha_900',"alpha_1220", "alpha_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(alpha_annual_mean, '../../data/alpha_timeline/Table_Mountain.alpha.csv')
```

# Graphs

In this section, the actual analysis is performed. For this purpose,
multiple graphs are created. First for the transmission, then for the
atmospheric optical depth and finally for the Ångström parameter.

## Transmission

### Overview transmission

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1925 - 1930)
Table_mountain.1925.1930.trans <- Table_Mountain_long|>
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.1925.1930.trans

Table_mountain.1925.trans <- Table_Mountain_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1924-01-01') & Date < as_date('1925-12-31')) |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.1925.trans
```

### Boxplot

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}
Table_mountain.boxplot <- Table_Mountain_long|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.boxplot
```

### Monthly aggregated atmospheric transmission

```{r Transmission_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}
transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
  label = c('348', '391', '446', '615', '1600')) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

```{r Annual_transmission, message=FALSE, warning=FALSE, error=FALSE}
annual_transmission <- trans_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(.3, 1))+
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1920 - 1930)
Table_mountain.1925.1930.od <- Table_Mountain_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

Table_mountain.1925.1930.od
```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Table_mountain.boxplot.od <- Table_Mountain_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.boxplot.od
```

### Monthly aggregated optical depth

```{r monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1)), 
  label = c('348', '446', '615','1600')) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
annual_od <- od_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '994', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1925 - 1930)
Table_mountain.alpha.1925.1930 <- Table_Mountain.alpha.long|>
  ggplot()+
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.1) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  labs(x = 'Time [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '1225', '1600')) +
  scale_y_continuous(limits = c(0, .1)) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.alpha.1925.1930
```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Table_mountain.boxplot.alpha <- Table_Mountain.alpha.long|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .1) +
  scale_x_discrete(labels = c('348', '391', '446', '497', '615', 
                                 '724','817', '1225', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Table_mountain.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
angstrom_overview <- Table_Mountain.alpha.long|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('348', '391', '446', '497', '615', 
                                 '724','817', '1225', '1600')) +  
  scale_y_continuous(limits = c(-.005, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  labs(x = 'Time [year]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(-.05, .2)) +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('348', '391', '446', '497', '615', 
                                 '724','817', '1225', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Table_mountain//Transmission/Table_mountain.1925.1930.trans.pdf',
    width = 8, height = 5)
Table_mountain.1925.1930.trans
dev.off()

pdf('../../analysis/Table_mountain//Transmission/Table_mountain.boxplot.pdf',
    width = 8, height = 5)
Table_mountain.boxplot
dev.off()

pdf('../../analysis/Table_mountain//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Table_mountain//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Table_mountain//Optical_depth/Table_mountain.1925.1930.od.pdf',
    width = 8, height = 5)
Table_mountain.1925.1930.od
dev.off()

pdf('../../analysis/Table_mountain//Optical_depth/Table_mountain.boxplot.od.pdf',
    width = 8, height = 5)
Table_mountain.boxplot.od
dev.off()

pdf('../../analysis/Table_mountain//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Table_mountain//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Table_mountain//Angstrom_parameter/Table_mountain.alpha.1925.1930.pdf',
    width = 8, height = 5)
Table_mountain.alpha.1925.1930
dev.off()

pdf('../../analysis/Table_mountain//Angstrom_parameter/Table_mountain.boxplot.alpha.pdf',
    width = 8, height = 5)
Table_mountain.boxplot.alpha
dev.off()

pdf('../../analysis/Table_mountain//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../../analysis/Table_mountain//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
