---
title: "Bachelorarbeit: Washington"
author: "Patrick Bigler"
date: "2023-09-02"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

# Introduction

## Read packages

```{r Package, message=FALSE, error=FALSE, warning=FALSE}
source("../../R/General/packages.R")

conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(yardstick::rmse)
conflicts_prefer(stringr::fixed)
```

## Read data

```{r Read_data, message=FALSE, error=FALSE, warning=FALSE}
Washington.1902.1907 <- read.delim("../../Data/Washington_1.txt")

Washington.1903.1907 <- read.delim("../../Data/Washington_2.txt")

################################################################################
# Washington
################################################################################
Washington.1902.1907 <- Washington.1902.1907|>
  dplyr::mutate('Date' = lubridate::ymd(paste(year, month, day, sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Washington.1902.1907$Location)))|>
  dplyr::select(-c('year', 'month', 'day'))

Washington.1902.1907 <- replace(Washington.1902.1907, Washington.1902.1907 == -999, NA)

################################################################################
Washington.1903.1907 <- Washington.1903.1907|>
  dplyr::mutate('Date' = lubridate::ymd(paste(year, month, day, sep = ' ')))|>
  dplyr::mutate(row = seq(1 : length(Washington.1903.1907$Location)))|>  
  dplyr::select(-c('year', 'month', 'day'))

Washington.1903.1907 <- replace(Washington.1903.1907, Washington.1903.1907 == -999, NA)

write_csv(Washington.1902.1907, '../../data/trans_Timeline/Washington.ok.csv')
```

## Slice and rebuild

Because there are shifts in the data sets, we must slice the table into
sub-tables. After that, we can correct the shift and build it all back
together. Simultaneously, we change the column names.

```{r Preparation_Washington, message=FALSE, error=FALSE, warning=FALSE}
Washington <- Washington.1902.1907|>
  dplyr::rename('lambda_400' = 'lambda1...m.', 'lambda_450' = 'lambda2...m.',
                'lambda_500' = 'lambda3...m.', 'lambda_600' = 'lambda4...m.',
                'lambda_700' = 'lambda5...m.','lambda_800' = 'lambda6...m.',
                'lambda_900' = 'lambda7...m.','lambda_1000' = 'lambda8...m.',
                'lambda_1200' = 'lambda9...m.','lambda_1600' = 'lambda10...m.',
                'trans_400' = 'transmission1....100.', 'trans_450' = 'transmission2....100.',
                'trans_500' = 'transmission3....100.','trans_600' = 'transmission4....100.',
                'trans_700' = 'transmission5....100.','trans_800' = 'transmission6....100.',
                'trans_900' = 'transmission7....100.','trans_1000' = 'transmission8....100.',
                'trans_1200' = 'transmission9....100.',
                'trans_1600' = 'transmission10....100.')|>
  dplyr::select(c('row', 'Date', starts_with('l'), starts_with('t')))
```

## Dataquality

-   Transform data frame into a long format.

-   Set levels

-   Substitute strange values with NA

```{r create_tables, message=FALSE, error=FALSE, warning=FALSE}
# We make some quality control. If a value bigger than 2, the it is a error (because the transmission is a values between 0 and 1 and the wavelength is between 0 and 1.6). Further, in the 1000nm wavelenght are most likely tipos. It seems quite impossible that there is such a outlier. Therefore, we filter these rows out. 
Washington <- Washington|>
  dplyr::mutate(across(3:22, ~ifelse(.x > 2, NA, .x)))

################################################################################
# Transmission (long format)
################################################################################
Washington_long <- Washington|>
  dplyr::select(c('Date', starts_with('t')))|>
  pivot_longer(cols = starts_with('t'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate('lambda' = rep(c('400', '450', '500', '600', '700', 
                                 '800','900', '1000', '1200', '1600'), times = 44))|>
  dplyr::mutate(variable = factor(variable,
                levels = c("trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|>
  dplyr::mutate(values = ifelse(values >= 1, NA, values)) |>
  dplyr::mutate(values = ifelse(values <= 0.1, NA, values))
################################################################################
transmission <- Washington_long|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_400' | variable == 'trans_450' |
                  variable == 'trans_600' | variable == 'trans_700' | variable == 'trans_1600')
################################################################################
trans_annual_mean <- Washington_long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))
################################################################################
# Optical Depth
################################################################################
Washington_od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))
################################################################################
optical_depth <- Washington_od|>
    dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
    group_by(month,variable)|>  
    summarize_at(vars(values), funs(min(., na.rm = TRUE), max(., na.rm = TRUE), 
                                  median(., na.rm = TRUE),
                                  mean(., na.rm = TRUE),
                                  sd(., na.rm = TRUE),
                                  quantile(., probs = .25, na.rm = TRUE),
                                  quantile(., probs = .75, na.rm = TRUE),
                                  IQR(.,na.rm = TRUE)))|>
  dplyr::filter(variable == 'trans_350' | variable == 'trans_400' | variable == 'trans_450' |
                  variable == 'trans_600' | variable == 'trans_700' 
                | variable == 'trans_1600')
################################################################################
od_annual_mean <- Washington_od|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("trans_350", "trans_400", "trans_450", "trans_500", 
                           "trans_600", "trans_700", "trans_800", "trans_900",
                           "trans_1000", "trans_1200", "trans_1600")))|> 
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(od_annual_mean, '../../data/od_Timeline/Washington.od.csv')
################################################################################
# Ågström parameter
################################################################################
Washington.alpha.long <- Washington|>
  dplyr::mutate(alpha_350 = NA,
    alpha_400 = -(log(Washington$trans_400) - log(Washington$trans_1000)) / log(400),
    alpha_450 = -(log(Washington$trans_450) - log(Washington$trans_1000)) / log(450),
    alpha_500 = -(log(Washington$trans_500) - log(Washington$trans_1000)) / log(500),
    alpha_600 = -(log(Washington$trans_600) - log(Washington$trans_1000)) / log(600),
    alpha_700 = -(log(Washington$trans_700) - log(Washington$trans_1000)) / log(700),
    alpha_800 = -(log(Washington$trans_800) - log(Washington$trans_1000)) / log(800),
    alpha_900 = -(log(Washington$trans_900) - log(Washington$trans_1000)) / log(900),
    alpha_1200 = -(log(Washington$trans_1200) - log(Washington$trans_1000)) / log(1200),
    alpha_1600 = -(log(Washington$trans_1600) - log(Washington$trans_1000)) / log(1600)) |>
  dplyr::select(c('row','Date', starts_with('a')))|>
  pivot_longer(cols = starts_with('a'),
               names_to = 'variable',
               values_to = 'values')|>
  dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1200", "alpha_1600")))  
################################################################################
alpha_annual_mean <- Washington.alpha.long|>
   dplyr::mutate(month = lubridate::month(Date, label = TRUE)) |> 
   dplyr::mutate(variable = factor(variable,
                levels = c("alpha_350", "alpha_400", "alpha_450", "alpha_500", 
                           "alpha_600", "alpha_700", "alpha_800", "alpha_900",
                           "alpha_1200", "alpha_1600")))|> 
    dplyr::filter(variable != 'trans_900') |>
    group_by(variable, month = lubridate::floor_date(Date, 'year'))|>
    summarise_at(vars(values), funs(mean(., na.rm = TRUE)))

write_csv(alpha_annual_mean, '../../data/alpha_timeline/Washington.alpha.csv')
```

# Graphs

## Transmission

### Overview transmission

Here you find a overview about the transmission data. Note that the 900nm
wavelength is not taken into account because there is only a low amount of
data.

Both figures have a smoothed line for estimate the trend.

```{r overview_transmission, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1902 - 1907)
Washington.1902.1907.trans <- Washington_long|>
  dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-02", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [WDC06A]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +    
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [1902-10-24]", hjust = 0, vjust = -0.2, angle = 90, alpha = .5) + 
  labs(x = 'Time [year]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.1902.1907.trans

################################################################################
# Zoom in (year 1903)
Washington.1903.trans <- Washington_long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1903-01-01') & Date < as_date('1903-12-31')) |>
  dplyr::filter(variable  != 'trans_900') |>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k = 5, fill = NA, align = 'center')) |>
ggplot()+
  #geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 0.2, label= "Santa Maria [1902-10-24]", hjust = 0, vjust = -0.2, angle = 90, alpha = .5) +
  labs(x = 'Time [month]', y = 'Transmission [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.1903.trans
```

### Boxplot

Here, you find a box-whiskers plot. Note that due to the Santa Maria
eruption in 1902 only data which are newer than 1905-01-01 are considered.

```{r Transmission_boxplot, message=FALSE, warning=FALSE, error=FALSE}
#function for theoretical calculation
source('../../R/General/theoretical_transmission.R')
# Create a sequenze with wavelenth between 0.1nm and 1.6nm
wavelenghts <- c(0.4, .45, .5, .6, .7, .8, .9, 1, 1.2, 1.6)
# Create a sequenze with wavelengths and zenith angle
values <- transmittance(wavelenghts)
# Put all values in a tibble
theoretical.values <- tibble("lambda" = seq(from = 1, to = 10, by = 1),
                             'normal_irradiation' = values)


Washington.boxplot <- Washington_long|>
    dplyr::filter((Date > as_date('1905-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = as.factor(variable), y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = "deepskyblue") +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = 0.1, alpha = .2) +
  geom_smooth(data = theoretical.values, aes(x = lambda, y = normal_irradiation), se = FALSE,
              linewidth = 0.5) +  
  scale_x_discrete(labels = c('400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot
```

### Monthly aggregated atmospheric transmission

Here, you find the monthly aggregated atmospheric transmission. There are
no errorbars during summer because there are only one measurement for each
month.

```{r Transmission_mothly_resolution, message=FALSE, warning=FALSE, error=FALSE}
transmission_overview <- transmission|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric transmission [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

transmission_overview
```

### Annual mean of the atmospheric transmission

Here you find the data aggregated in an annual mean.

```{r Annual_transmission, message=FALSE, warning=FALSE, error=FALSE}
annual_transmission <- trans_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-19", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) +
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [WDC06A]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +  
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1)+  
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 0, label= "Santa Maria [1902-10-24]", hjust = 0, vjust = -0.2, angle = 90, alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric transmission [ ]') +
  scale_y_continuous(limits = c(0, 1))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_transmission
```

## Optical Depth

### Overview optical depth

```{r Overview_od, warning=FALSE, error=FALSE, message=FALSE}
################################################################################
# Overview (1902 - 1907)
Washington.1902.1907.od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  #dplyr::filter(variable  != 'trans_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-19", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = 1.2, label= "Santa Maria [WDC06A]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 1.2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  labs(x = 'Time [year]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))  

Washington.1902.1907.od

################################################################################
# Zoom in (year 1903)
Washington.1903.od <- Washington_long|>
  dplyr::mutate_at(c('values'), ~-log(.))|>
  dplyr::filter(Date > as_date('1903-01-01') & Date < as_date('1904-12-31')) |>  
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  # Adapt labels
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 1.2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2, angle = 90, alpha = .5) +
  labs(x = 'Time [month]', y = 'Atmospheric optical depth [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('350', '400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))    

Washington.1903.od


```

### Boxplot

```{r Boxplot_od, message=FALSE, error=FALSE, warning=FALSE}
Washington.boxplot.od <- Washington_long|>
    dplyr::mutate_at(c('values'), ~-log(.))|>
    #dplyr::filter(variable  != 'trans_900') |>  
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .2) +
  scale_x_discrete(labels = c('400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot.od
```

### Monthly aggregated optical depth

Here, you find the monthly aggregated atmospheric optical depth. There are
no errorbars during summer because there are only one measurement for each
month.

```{r monthly_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
optical_depth_overview <- optical_depth|>
  ggplot() +
  geom_point(aes(x = month, y = mean, color = variable)) +
  geom_line(aes(x = month, y = mean, color = variable, group = variable)) +
  geom_errorbar(aes(x = month, ymin = mean - sd, ymax = mean + sd), width = .1) +
  guides(color = guide_legend(title = "Wavelength [nm]")) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  labs(x = 'Time [month]', y = 'Monthly aggregated atmospheric optical depth [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

optical_depth_overview
```

### Annual mean of the optical depth

```{r Annual_aggregated_od, message=FALSE, error=FALSE, warning=FALSE}
annual_od <- od_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-19", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = 1.2, label= "Santa Maria [WDC06A]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable)) +
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = 1.2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the atmospheric optical depth [ ]') +
  scale_y_continuous(limits = c(0, 1.2))+
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_od
```

## Angström Parameter

### Overview (1905 - 1920)

```{r Overview_alpha, message=FALSE, error=FALSE, warning=FALSE}
################################################################################
# Overview (1905 - 1920)
Washington.alpha.1902.1907 <- Washington.alpha.long|>
  dplyr::filter(variable  != 'alpha_900') |>  
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-19", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = .2, label= "Santa Maria [WDC06A]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) + 
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_smooth(aes(x = Date, y = values, color = variable), se = FALSE) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = .2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Ångström paramter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600')) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.alpha.1902.1907

################################################################################
# Zoom in (year 1912)

Washington.1903.alpha <- Washington.alpha.long|>
  # Change dates in the filter to zoom into another time period
  dplyr::filter(Date > as_date('1903-01-01') & Date < as_date('1903-12-31'))|>  
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>
ggplot()+
  geom_line(aes(x = Date, y = rolling_avg, color = variable)) +
  geom_point(aes(x = Date, y = values, color = variable), alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = .2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2,angle = 90,alpha = 0.5) +
  labs(x = 'Time [month]', y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "varidis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), label = c('400', '450', '500', '600',
                                                    '700', '800', '1000', '1200', '1600') ) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.1903.alpha
```

### Boxplot

```{r Boxplot_alpha, message=FALSE, error=FALSE, warning=FALSE}
Washington.boxplot.alpha <- Washington.alpha.long|>
    dplyr::filter((Date > as_date('1903-01-01'))) |>
ggplot()+
  geom_boxplot(aes(x = variable, y = values),
  notch = TRUE, outlier.alpha = 1, outlier.colour = 'red', fill = 'deepskyblue') +
  stat_boxplot(aes(x = variable, y = values),
  geom='errorbar', linetype = 1, width = 0.5) +
  geom_jitter(aes(x = variable, y = values), size = .5, width = .1, alpha = .2) +
  scale_x_discrete(labels = c('350', '400', '450', '500', '600', '700', '800', 
                              '900','1000', '1200', '1600')) +
  labs(x = 'Wavelength [nm]', y = 'Ångström parameter [ ]') +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

Washington.boxplot.alpha
```

### Monthly aggregated Ångström parameter

```{r Monhtly_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
angstrom_overview <- Washington.alpha.long|>
  dplyr::filter(Date > as_date('1903-01-01') & Date < as_date('1903-12-31'))|>
  #dplyr::filter(variable != 'alpha_900')|>
  group_by(variable) |>
  dplyr::mutate(rolling_avg = rollmean(values, k=5, fill=NA, align='center')) |>  
  ggplot(aes(x = Date, y = values, color = variable)) +
  geom_point(aes(y = values, color = variable), alpha = 0.2) +
  geom_line(aes(y = rolling_avg, color = variable)) +
  labs(x = 'Time [month]', 
       y = 'Ångström parameter [ ]') +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3,
  alpha = 1), title = "Wavelength [nm]"), labels = c('400','450','500',
                                                     '600','700','800','900','1200','1600')) +  
  scale_y_continuous(limits = c(0.05, .2))+  
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

angstrom_overview
```

### Annual mean of the Ångström parameter

```{r Annual_aggregated_alpha, message=FALSE, error=FALSE, warning=FALSE}
annual_alpha <- alpha_annual_mean|>
  ggplot()+
  geom_rect(aes(xmin = as.Date("1902-10-19", format = '%Y-%m-%d'), 
                xmax = as.Date("1904-04-20", format = '%Y-%m-%d'), 
                ymin = -Inf, ymax = Inf), 
          color = "lightskyblue1", alpha = 0.01, fill = "lightskyblue1", linewidth = 0.2) + 
  annotate("text", x = as.Date("1904-04-20", format = '%Y-%m-%d'),
  y = .2, label= "Santa Maria [WDC06A]", hjust = 1, vjust = -0.2, angle = 90, alpha = 0.5) +   
  geom_point(aes(x = month, y = values, color = variable))+
  geom_line(aes(x = month, y = values, color = variable), size = 0.1) +  
  geom_vline(xintercept = as.numeric(as.Date("1902-10-24")), linetype = 'dotted') +
  annotate("text", x = as.Date("1902-10-24", format = '%Y-%m-%d'),
  y = .2, label= "Santa Maria [1902-10-24]", hjust = 1, vjust = -0.2,angle = 90, alpha = 0.5) +
  labs(x = 'Time [year]', y = 'Annual mean of the Ångström parameter [ ]') +
  scale_y_continuous(limits = c(-.005, .2)) +
  scale_color_viridis_d(option = "viridis",
  guide = guide_legend(override.aes = list(size = 3, alpha = 1), title = "Wavelength [nm]")) +
  theme_light() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))

annual_alpha
```

# PDFs

## Transmission

```{r PDF_transmission, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Washington//Transmission/Washington.1902.1907.trans.pdf',
    width = 8, height = 5)
Washington.1902.1907.trans
dev.off()

pdf('../../analysis/Washington//Transmission/Washington.1903.trans.pdf',
    width = 8, height = 5)
Washington.1903.trans
dev.off()

pdf('../../analysis/Washington//Transmission/Washington.boxplot.pdf',
    width = 8, height = 5)
Washington.boxplot
dev.off()

pdf('../../analysis/Washington//Transmission/transmission_overview.pdf',
    width = 8, height = 5)
transmission_overview
dev.off()

pdf('../../analysis/Washington//Transmission/annual_transmission.pdf',
    width = 8, height = 5)
annual_transmission
dev.off()
```

## Optical depth

```{r PDF_od, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Washington//Optical_depth/Washington.1902.1907.od.pdf',
    width = 8, height = 5)
Washington.1902.1907.od
dev.off()

pdf('../../analysis/Washington//Optical_depth/Washington.1903.od .pdf',
    width = 8, height = 5)
Washington.1903.od 
dev.off()

pdf('../../analysis/Washington//Optical_depth/Washington.boxplot.alpha.pdf',
    width = 8, height = 5)
Washington.boxplot.alpha
dev.off()

pdf('../../analysis/Washington//Optical_depth/optical_depth_overview.pdf',
    width = 8, height = 5)
optical_depth_overview
dev.off()

pdf('../../analysis/Washington//Optical_depth/annual_od.pdf',
    width = 8, height = 5)
annual_od
dev.off()
```

## Ångström parameter

```{r PDF_alpha, message=FALSE, error=FALSE, warning=FALSE}
pdf('../../analysis/Washington//Angstrom_parameter/Washington.alpha.1902.1907.pdf',
    width = 8, height = 5)
Washington.alpha.1902.1907
dev.off()

pdf('../../analysis/Washington//Angstrom_parameter/Washington.1903.alpha.pdf',
    width = 8, height = 5)
Washington.1903.alpha
dev.off()

pdf('../../analysis/Washington//Angstrom_parameter/Washington.boxplot.alpha.pdf',
    width = 8, height = 5)
Washington.boxplot.alpha
dev.off()

pdf('../../analysis/Washington//Angstrom_parameter/angstrom_overview.pdf',
    width = 8, height = 5)
angstrom_overview
dev.off()

pdf('../../analysis/Washington//Angstrom_parameter/annual_alpha.pdf',
    width = 8, height = 5)
annual_alpha
dev.off()
```
